---
title: "H~2~: Effect of anti-NGO crackdown on aid contentiousness"
format:
  html:
    code-fold: true
    toc-depth: 5
    knitr:
      opts_chunk:
        out.width: "80%"
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(digits = 3, width = 120,
        dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(brms)
library(tidybayes)
library(broom)
library(broom.mixed)
library(modelsummary)
library(marginaleffects)
library(patchwork)
library(scales)
library(ggdist)
library(ggtext)
library(ggh4x)
library(extraDistr)
library(kableExtra)
library(glue)
library(here)

tar_config_set(store = here::here('_targets'),
               script = here::here('_targets.R'))

set.seed(1234)

# Load stuff from targets
# Plotting functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(tbl_functions), .GlobalEnv))
set_annotation_fonts()

# Tell bayesplot to use the sunset palette for things like pp_check()
bayesplot::color_scheme_set(clrs$Sunset[2:7])

# Data
df_country_aid <- tar_read(country_aid_final)
df_country_aid_laws <- filter(df_country_aid, laws)

# Treatment models
tar_load(c(m_purpose_treatment_total, m_purpose_treatment_advocacy, 
           m_purpose_treatment_entry, m_purpose_treatment_funding, 
           m_purpose_treatment_ccsi, m_purpose_treatment_repress))

# IPTW data
tar_load(c(df_purpose_iptw_total, df_purpose_iptw_advocacy, 
           df_purpose_iptw_entry, df_purpose_iptw_funding,
           df_purpose_iptw_ccsi, df_purpose_iptw_repress))

# Outcome models
tar_load(c(m_purpose_outcome_total, m_purpose_outcome_advocacy, 
           m_purpose_outcome_entry, m_purpose_outcome_funding,
           m_purpose_outcome_ccsi, m_purpose_outcome_repress))

# Marginal/conditional effects
tar_load(c(mfx_purpose_cfx_multiple, mfx_purpose_cfx_single))

# Results tables
tar_load(c(models_tbl_h2_treatment_num, models_tbl_h2_treatment_denom))
tar_load(c(models_tbl_h2_outcome_dejure, models_tbl_h2_outcome_defacto))
```

```{r modelsummary-settings}
invisible(list2env(tar_read(modelsummary_functions), .GlobalEnv))

treatment_names <- c("Treatment", "Total barriers (t)", "Barriers to advocacy (t)", 
                     "Barriers to entry (t)", "Barriers to funding (t)", "CCSI (t)",
                     "CS repression (t)")
treatment_rows <- as.data.frame(t(treatment_names))
attr(treatment_rows, "position") <- 1

outcome_names <- c("Treatment", "Total barriers (t)", "Barriers to advocacy (t)", 
                   "Barriers to entry (t)", "Barriers to funding (t)")
outcome_rows <- as.data.frame(t(outcome_names))
attr(outcome_rows, "position") <- 1
```

# Weight models

## General idea

See the ["Weight models—General idea" section from the total aid page](models_total-aid.qmd#general-idea) for an explanation of the intuition behind how to create these stabilized weights.

## Actual models

We identify our time-varying and time-invariant confounders based on [our causal model and *do*-calculus logic](causal-model.qmd#final-variables-to-use), and we deal with the panel structure of the data by including random intercepts for country, and both a population-level trend and random slopes for year. We use [generic weakly informative priors](https://mc-stan.org/users/documentation/case-studies/weakly_informative_shapes.html) for our model parameters.

### Numerator

Our numerator models look like this (but with the actual treatment variable replacing `treatment`, like `barriers_total`, `advocacy`, and so on):

```{r fake-numerator, eval=FALSE}
#| code-fold: show
bf(treatment ~ treatment_lag1 + treatment_lag2_cumsum + (1 | gwcode))
```

Or more formally:

$$
\begin{aligned}
\text{Treatment}_{it_j} &\sim \mathcal{N}(\mu_{it_j}, \sigma_y) \\
\mu_{it_j} &= (\beta_0 + b_{0_j}) + \beta_1 \text{Treatment}_{i, t-1_j} + \textstyle{\sum_{\tau = (t-2)}^{t}} \text{Treatment}_{i\tau} \\
b_{0_j} &\sim \mathcal{N}(0, \sigma_0) \\
\\
\beta_0, \beta_1 &\sim \operatorname{Student~\textit{t}\,}(\nu = 3, \mu = 0, \sigma = 1.5) \\
\sigma_y, \sigma_0 &\sim \operatorname{Exponential}(1)
\end{aligned}
$$

### Denominator

Our denominator models look like this (but again with the actual treatment variable replacing `treatment`):

```{r fake-denominator, eval=FALSE}
#| code-fold: show
bf(treatment ~ treatment_lag1 + treatment_lag2_cumsum + 
     # Lagged outcome
     prop_contentious_lag1 +
     # Human rights and politics
     v2x_polyarchy + v2x_corr + v2x_rule + v2x_civlib + v2x_clphy + v2x_clpriv +
     # Economics and development
     gdpcap_log_z + un_trade_pct_gdp + v2peedueq + v2pehealth + e_peinfmor +
     # Conflict and disasters
     internal_conflict_past_5 + natural_dis_count +
     # Time and country effects
     year_c + (1 + year_c | gwcode))
```

Or more formally:

$$
\begin{aligned}
\text{Treatment}_{it_j} \sim&\ \mathcal{N}(\mu_{it_j}, \sigma_y) \\
\mu_{it_j} =&\ (\beta_0 + b_{0_j}) + \beta_1\, \text{Treatment}_{i, t-1_j} + \beta_2\, \textstyle{\sum_{\tau = (t-2)}^{t}} \text{Treatment}_{i\tau} + \\
&\ \beta_3\, \text{Proportion of contentious aid}_{i,t-1_j} + \beta_{4 \ldots 9}\, \text{Human rights \& politics}_{it_j} + \\
&\ \beta_{10 \ldots 14}\, \text{Economics \& development} + \beta_{15, 16}\, \text{Conflict \& disasters}_{it_j} + \\
&\ (\beta_{17} + b_{17_j})\, \text{Year}_{it_j} \\
\left(
  \begin{array}{c} 
  b_{0_j} \\
  b_{17_j}
  \end{array}
\right) 
\sim&\ \text{MV}\,\mathcal{N}
\left[
  \left(
    \begin{array}{c}
    0 \\
    0 \\
    \end{array}
  \right)
  , \,
  \left(
  \begin{array}{cc}
     \sigma^2_{0} & \rho_{0, 17}\, \sigma_{0} \sigma_{17} \\ 
     \cdots & \sigma^2_{17}
  \end{array}
\right)
\right] \\
\\
\beta_0 \ldots \beta_{17} \sim&\ \operatorname{Student~\textit{t}\,}(\nu = 3, \mu = 0, \sigma = 1.5) \\
\sigma_y, \sigma_0, \sigma_{17} \sim&\ \operatorname{Exponential}(1) \\
\rho \sim&\ \operatorname{LKJ}(2)
\end{aligned}
$$


## MCMC diagnostics

Again, as a check to make sure these weight models converged, here are some visual diagnostics for the total barriers treatment. All the other models look basically the same as these.

### Numerator

::: {.panel-tabset}

#### Trace plots

```{r plot-num-trace, warning=FALSE}
#| out-width: 80%
m_purpose_treatment_total$model_num %>% 
  gather_draws(`^b_.*|^sd_.*|^sigma`, regex = TRUE) %>% 
  ggplot(aes(x = .iteration, y = .value, color = factor(.chain))) +
  geom_line(linewidth = 0.1) +
  scale_color_manual(values = clrs$Sunset[3:6]) +
  facet_wrap(vars(.variable), scales = "free_y") +
  theme_donors()
```

#### Trank plots

```{r plot-num-trank, warning=FALSE}
#| out-width: 80%
m_purpose_treatment_total$model_num %>% 
  gather_draws(`^b_.*|^sd_.*|^sigma`, regex = TRUE) %>% 
  group_by(.variable) %>% 
  mutate(draw_rank = rank(.value)) %>% 
  ggplot(aes(x = draw_rank, color = factor(.chain))) +
  stat_bin(geom = "step", binwidth = 500, position = position_identity(), boundary = 0) +
  scale_color_manual(values = clrs$Sunset[3:6]) +
  facet_wrap(vars(.variable), scales = "free_y") +
  theme_donors() +
  theme(axis.text.y = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank())
```

#### Posterior predictive check

```{r plot-num-ppcheck}
#| out-width: 80%
withr::with_seed(1234, {
  pp_check(m_purpose_treatment_total$model_num, ndraws = 20) +
    labs(x = "Total NGO barriers",
         title = "Numerator model") +
    theme_donors()
})
```

:::

### Denominator

::: {.panel-tabset}

#### Trace plots

```{r plot-denom-trace, warning=FALSE, fig.width=10, fig.height=7}
#| out-width: 100%
m_purpose_treatment_total$model_denom %>% 
  gather_draws(`^b_.*|^sd_.*|^cor_.*|^sigma`, regex = TRUE) %>% 
  ggplot(aes(x = .iteration, y = .value, color = factor(.chain))) +
  geom_line(linewidth = 0.1) +
  scale_color_manual(values = clrs$Sunset[3:6]) +
  facet_wrap(vars(.variable), scales = "free_y") +
  theme_donors()
```

#### Trank plots

```{r plot-denom-trank, warning=FALSE, fig.width=10, fig.height=7}
#| out-width: 100%
m_purpose_treatment_total$model_denom %>% 
  gather_draws(`^b_.*|^sd_.*|^cor_.*|^sigma`, regex = TRUE) %>% 
  group_by(.variable) %>% 
  mutate(draw_rank = rank(.value)) %>% 
  ggplot(aes(x = draw_rank, color = factor(.chain))) +
  stat_bin(geom = "step", binwidth = 500, position = position_identity(), boundary = 0) +
  scale_color_manual(values = clrs$Sunset[3:6]) +
  facet_wrap(vars(.variable), scales = "free_y") +
  theme_donors() +
  theme(axis.text.y = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank())
```

#### Posterior predictive check

```{r plot-denom-ppcheck}
#| out-width: 80%
withr::with_seed(1234, {
  pp_check(m_purpose_treatment_total$model_denom, ndraws = 20) +
    labs(x = "Total NGO barriers",
         title = "Denominator model") +
    theme_donors()
})
```

:::


## Check weights

Again, IPTWs should generally have a mean of 1 and shouldn't be too incredibly high.

::: {.panel-tabset}
### Total barriers

The max weight here is `r round(max(df_purpose_iptw_total$iptw), 0)`, but as with H~1~ there are only a few observations with weights that high. The average is `r round(mean(df_purpose_iptw_total$iptw), 2)` and the median is `r round(median(df_purpose_iptw_total$iptw), 2)`, which are both close to 1, which is good.

```{r iptws-total-purpose}
#| code-fold: show
summary(df_purpose_iptw_total$iptw)
```

```{r plot-iptws-total-purpose}
df_purpose_iptw_total %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(binwidth = 0.5, boundary = 0) +
  theme_donors()
```

### Advocacy

The max weight here is `r round(max(df_purpose_iptw_advocacy$iptw), 0)`, and the average is `r round(mean(df_purpose_iptw_advocacy$iptw), 2)`, so we're good still.

```{r iptws-advocacy}
#| code-fold: show
summary(df_purpose_iptw_advocacy$iptw)
```

```{r plot-iptws-advocacy}
df_purpose_iptw_advocacy %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(binwidth = 0.5, boundary = 0) +
  theme_donors()
```

### Entry

The max weight here is `r round(max(df_purpose_iptw_entry$iptw), 0)` and the average is `r round(mean(df_purpose_iptw_entry$iptw), 2)`, so everything's still great.

```{r iptws-entry}
#| code-fold: show
summary(df_purpose_iptw_entry$iptw)
```

```{r plot-iptws-entry}
df_purpose_iptw_entry %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(binwidth = 0.5, boundary = 0) +
  theme_donors()
```

### Funding

The max weight is `r round(max(df_purpose_iptw_funding$iptw), 0)` and the average is `r round(mean(df_purpose_iptw_funding$iptw), 2)`—great!

```{r iptws-funding}
#| code-fold: show
summary(df_purpose_iptw_funding$iptw)
```

```{r plot-iptws-funding}
df_purpose_iptw_funding %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(binwidth = 0.5, boundary = 0) +
  theme_donors()
```

### Core civil society index

lol these blow up again; the max weight is `r label_comma()(max(df_purpose_iptw_ccsi$iptw))`.

```{r iptws-ccsi}
#| code-fold: show
summary(df_purpose_iptw_ccsi$iptw)
```

There aren't a lot of observations with weights that high though—only 100ish:

```{r show-threshold-counts-iptws-ccsi}
#| code-fold: show
df_purpose_iptw_ccsi %>% count(iptw >= 50)
df_purpose_iptw_ccsi %>% count(iptw >= 500)
```

We truncate these weights at 50.

```{r plot-iptws-ccsi}
plot_iptw_ccsi <- bind_rows(
  df_purpose_iptw_ccsi %>% mutate(threshold = 50, iptw = ifelse(iptw > threshold, threshold, iptw)),
  df_purpose_iptw_ccsi %>% mutate(threshold = 500, iptw = ifelse(iptw > threshold, threshold, iptw))
) %>% 
  mutate(threshold = paste0("Truncated at ", threshold),
         threshold = fct_inorder(threshold))

plot_iptw_ccsi %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(bins = 50, boundary = 0) +
  facet_wrap(vars(threshold), scales = "free_x") +
  theme_donors()
```

### Civil society repression

These weights are also horrendous, with a maximum weight of `r label_comma()(max(df_purpose_iptw_repress$iptw))`.

```{r iptws-csrepress}
#| code-fold: show
summary(df_purpose_iptw_repress$iptw)
```

As with the core civil society index, there aren't a lot of observations with weights that high:

```{r show-threshold-counts-iptws-csrepress}
#| code-fold: show
df_purpose_iptw_repress %>% count(iptw >= 50)
df_purpose_iptw_repress %>% count(iptw >= 500)
```

So we truncate these weights at 50 again. Since the results from the core civil society models are basically the same when truncating at 500, we only use a truncation point of 50 here.

```{r plot-iptws-csrepress}
df_purpose_iptw_ccsi %>% 
  mutate(threshold = 50, iptw = ifelse(iptw > threshold, threshold, iptw)) %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(bins = 50, boundary = 0) +
  theme_donors()
```
:::


## Results

These are less important since we just use these treatment models to generate weights *and* because interpreting each coefficient when trying to isolate causal effects is unimportant [@WestreichGreenland:2013; @KeeleStevensonElwert:2020].

::: {.panel-tabset}

### Numerator

```{r tbl-h2-num, warning=FALSE}
#| tbl-cap: Results from all numerator models
models_tbl_h2_treatment_num <- models_tbl_h2_treatment_num %>% 
  set_names(1:length(.))

notes <- c(
  "Posterior medians; 95% credible intervals in brackets", 
  "Total \\(R^2\\) considers the variance of both population and group effects", 
  "Marginal \\(R^2\\) only takes population effects into account"
)

modelsummary(models_tbl_h2_treatment_num,
             estimate = "{estimate}",
             statistic = "[{conf.low}, {conf.high}]",
             add_rows = treatment_rows,
             coef_map = coefs_num,
             gof_map = gofs,
             output = "kableExtra",
             fmt =  list(estimate = 2, conf.low = 2, conf.high = 2)) %>% 
  row_spec(1, bold = TRUE) %>% 
  kable_styling(htmltable_class = "table-sm light-border")
```

### Denominator

```{r tbl-h2-denom, warning=FALSE}
#| tbl-cap: Results from all numerator models
models_tbl_h2_treatment_denom <- models_tbl_h2_treatment_denom %>% 
  set_names(1:length(.))

notes <- c(
  "Posterior medians; 95% credible intervals in brackets", 
  "Total \\(R^2\\) considers the variance of both population and group effects", 
  "Marginal \\(R^2\\) only takes population effects into account"
)

modelsummary(models_tbl_h2_treatment_denom,
             estimate = "{estimate}",
             statistic = "[{conf.low}, {conf.high}]",
             add_rows = treatment_rows,
             coef_map = coefs_denom,
             gof_map = gofs,
             fmt =  list(estimate = 2, conf.low = 2, conf.high = 2),
             notes = notes) %>% 
  row_spec(1, bold = TRUE) %>% 
  kable_styling(htmltable_class = "table-sm light-border")
```

:::


# Outcome models

Our outcome variable for this hypothesis is the proportion of aid allocated to contentious issues, which is (1) bounded between 0% and 100% and (2) has a lot of zeros.

```{r tbl-zero-summary}
#| tbl-cap: 0s in proportion of contentious aid
df_country_aid_laws %>% 
  count(is_zero = prop_contentious == 0) %>% 
  mutate(Outcome = "Proportion of contentious aid") %>% 
  mutate(`Number of 0s` = glue("{n[2]} / {sum(n)}")) %>% 
  mutate(`Proportion of 0s` = label_percent(accuracy = 0.1)(n / sum(n))) %>% 
  filter(is_zero) %>% select(-is_zero, -n) %>% 
  kbl(align = c("l", "c", "c")) %>% 
  kable_styling(htmltable_class = "table table-sm",
                full_width = FALSE)
```

```{r plot-zero-purpose, fig.width=6, fig.height=3.5}
#| out-width: 80%
df_country_aid_laws %>%
  mutate(is_zero = prop_contentious == 0) %>% 
  mutate(prop_contentious = ifelse(is_zero, -0.01, prop_contentious))  %>%  
  ggplot(aes(x = prop_contentious)) +
  geom_histogram(aes(fill = is_zero), binwidth = 0.05, 
                 linewidth = 0.25, boundary = 0, color = "white") +
  geom_vline(xintercept = 0) + 
  scale_x_continuous(labels = label_percent()) +
  scale_y_continuous(labels = label_comma()) +
  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[8]), 
                    guide = guide_legend(reverse = TRUE)) +
  labs(x = "Proportion of contentious aid", y = "Count", fill = "Is zero?") +
  theme_donors() +
  theme(legend.position = "bottom")
```

Because of this distribution, we use a zero-inflated beta family to model the outcome. [This guide to working with tricky outcomes with lots of zeros](model-tricky-outcomes.qmd#zero-inflated-models-proportions) explores all the intricacies of zero-inflated beta families, so we won't go into tons of detail here.

Following our marginal structural model approach, we need to run a model weighted by the stabilized inverse probability weights that includes covariates for lagged treatment $X_{i, t-1}$, treatment history $\sum_{\tau = (t-2)}^{t} X_{i\tau}$, and non-time-varying confounders $Z_i$. We expand on this approach to account for the panel structure of the data by using a multilevel hierarchical model with country-specific intercepts and a year trend with country-specific offsets (following yet another guide I wrote for this project, [this one on multilevel panel data](https://www.andrewheiss.com/blog/2021/12/01/multilevel-models-panel-data-guide/)). We center the year at 2000 so that (1) the intercept is interpretable [@Schielzeth:2010] and (2) the MCMC simulation runs faster and more efficiently [@McElreath:2020 §13.4, pp. 420–422]. 

As with foreign aid, we’re not entirely sure what the actual underlying zero process is for the proportion of contentious aid, but from looking at the data, we know that there’s a time component—in the early 2000s, very few countries received no contentious aid. We thus model the zero-inflated part of the model with year and year squared since the year trend is parabolic and nonlinear.

```{r plot-prop-zero-zi, fig.width=6, fig.height=3.5}
#| out-width: 80%
df_country_aid_laws %>% 
  group_by(year) %>% 
  summarize(prop_zero = mean(prop_contentious == 0)) %>% 
  ggplot(aes(x = year, y = prop_zero)) +
  geom_line(linewidth = 0.5, color = "grey70") +
  geom_point(size = 1) + 
  geom_smooth(aes(color = "y = x"), method = "lm", 
              formula = y ~ x, se = FALSE) +
  geom_smooth(aes(color = "y = x + x<sup>2</sup>"), method = "lm", 
              formula = y ~ x + I(x^2), se = FALSE) +
  scale_y_continuous(labels = label_percent()) +
  scale_color_manual(values = clrs$Prism[c(3, 11)]) +
  labs(x = NULL, y = "Proportion of countries\nwith zero contentious aid",
       color = NULL) +
  theme_donors() +
  theme(legend.text = element_markdown())
```


## Formal model and priors

Our final model looks like this (again with `treatment` replaced by the actual treatment column):

```{r fake-outcome, eval=FALSE}
#| code-fold: show
bf(prop_contentious | weights(iptw) ~ treatment_lag1 + treatment_lag2_cumsum +
     year_c + (1 + year_c | gwcode),
   zi ~ year_c + I(year_c^2))
```

Or more formally:

::: {.column-page-inset-right}

$$
\begin{aligned}
&\ \mathrlap{\textbf{Zero-inflated model of proportion $i$ across time $t$ within each country $j$}} \\
\text{Proportion}_{it_j} \sim&\ \mathrlap{\begin{cases}
0 & \text{with probability } \pi_{it} + [(1 - \pi_{it}) \times \operatorname{Beta}(0 \mid \mu_{it_j}, \phi_y)] \\[4pt]
\operatorname{Beta}(\mu_{it_j}, \phi_y) & \text{with probability } (1 - \pi_{it}) \times \operatorname{Beta}(\text{Proportion}_{it_j} \mid \mu_{it_j}, \phi_y)
\end{cases}} \\
\\
&\ \textbf{Models for distribution parameters} \\
\operatorname{logit}(\pi_{it}) =&\ \gamma_0 + \gamma_1 \text{Year}_{it} + \gamma_2 \text{Year}^2_{it} & \text{Zero-inflation process} \\[4pt]
\operatorname{logit}(\mu_{it_j}) =&\ \text{IPTW}_{i, t-1_j} \times \Bigl[ (\beta_0 + b_{0_j}) + \beta_1\, \text{Treatment}_{i, t-1_j} + \\
&\ \beta_2\, \textstyle{\sum_{\tau = (t-2)}^{t}} \text{Treatment}_{i\tau} + (\beta_3 + b_{3_j}) \text{Year}_{it_j} \Bigr] & \text{Within-country variation} \\[4pt]
\left(
  \begin{array}{c} 
  b_{0_j} \\
  b_{3_j}
  \end{array}
\right) 
\sim&\ \text{MV}\,\mathcal{N}
\left[
  \left(
    \begin{array}{c}
    0 \\
    0 \\
    \end{array}
  \right)
  , \,
  \left(
  \begin{array}{cc}
     \sigma^2_{0} & \rho_{0, 3}\, \sigma_{0} \sigma_{3} \\ 
     \cdots & \sigma^2_{3}
  \end{array}
\right)
\right] & \text{Variability in average intercepts and slopes} \\
\\
&\ \textbf{Priors} \\
\gamma_0 \sim&\ \text{Student $t$}(\nu = 3, \mu = 0, \sigma = 1.5) & \text{Prior for intercept in zero-inflated model} \\
\gamma_1, \gamma_2 \sim&\ \text{Student $t$}(3, 0, 1.5) & \text{Prior for year effect in zero-inflated model} \\
\beta_0 \sim&\ \text{Student $t$}(3, 0, 1.5) & \text{Prior for global average proportion} \\
\beta_1, \beta_2, \beta_3 \sim&\ \text{Student $t$}(3, 0, 1.5) & \text{Prior for global effects} \\
\phi_y \sim&\ \operatorname{Exponential}(1) & \text{Prior for within-country dispersion} \\
\sigma_0, \sigma_3 \sim&\ \operatorname{Exponential}(1) & \text{Prior for within-country variability} \\
\rho \sim&\ \operatorname{LKJ}(2) & \text{Prior for between-country variability}
\end{aligned}
$$

:::

Here's what those priors look like:

```{r plot-outcome-priors, fig.width=7, fig.height=5.5}
design <- "
  AAABBB
  CCCDDD
  EEFFGG
"

m_purpose_outcome_total$priors %>% 
  parse_dist() %>% 
  # K = dimension of correlation matrix; 
  # ours is 2x2 here because we have one random slope
  marginalize_lkjcorr(K = 2) %>%
  mutate(nice_title = glue("**{class}**: {prior}"),
         stage = ifelse(dpar == "zi", "Zero-inflated part (π)", "Beta part (µ and φ)")) %>% 
  mutate(nice_title = fct_inorder(nice_title),
         stage = fct_rev(fct_inorder(stage))) %>% 
  ggplot(aes(y = 0, dist = .dist, args = .args, fill = prior)) +
  stat_slab(normalize = "panels") +
  scale_fill_manual(values = clrs$Prism[1:6]) +
  facet_manual(vars(stage, nice_title), design = design, scales = "free_x",
               strip = strip_nested(background_x = list(element_rect(fill = "grey92"), NULL),
                                    by_layer_x = TRUE)) +
  guides(fill = "none") +
  labs(x = NULL, y = NULL) +
  theme_donors(prior = TRUE) +
  theme(strip.text = element_markdown())
```

## MCMC diagnostics

To check that everything converged nicely, we check some diagnostics for the outcome models for the total barriers treatment. All the other models look basically the same as this—everything's fine.

::: {.panel-tabset}

### Trace plots

```{r plot-outcome-trace, warning=FALSE}
#| out-width: 80%
m_purpose_outcome_total$model %>% 
  gather_draws(`^b_.*|^sd_.*|^phi`, regex = TRUE) %>% 
  ggplot(aes(x = .iteration, y = .value, color = factor(.chain))) +
  geom_line(linewidth = 0.1) +
  scale_color_manual(values = clrs$Sunset[3:6]) +
  facet_wrap(vars(.variable), scales = "free_y") +
  theme_donors()
```

### Trank plots

```{r plot-outcome-trank, warning=FALSE}
#| out-width: 80%
m_purpose_outcome_total$model %>% 
  gather_draws(`^b_.*|^sd_.*|^phi`, regex = TRUE) %>% 
  group_by(.variable) %>% 
  mutate(draw_rank = rank(.value)) %>% 
  ggplot(aes(x = draw_rank, color = factor(.chain))) +
  stat_bin(geom = "step", binwidth = 1000, position = position_identity(), boundary = 0) +
  scale_color_manual(values = clrs$Sunset[3:6]) +
  facet_wrap(vars(.variable), scales = "free_y") +
  theme_donors() +
  theme(axis.text.y = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank())
```

### Posterior predictive check

```{r plot-outcome-ppcheck, message=FALSE}
#| out-width: 80%
withr::with_seed(1234, {
  pp_check(m_purpose_outcome_total$model, ndraws = 20) +
    labs(x = "Proportion of contentious aid",
         title = "Outcome model") +
    theme_donors() +
    coord_cartesian(xlim = c(0, 1))
})
```

:::

## Analyzing the posterior

### Average treatment effects (global analysis)

In this project we care most about *conditional effects*, or the effect of the treatment in a typical country, or effect of the treatment when all country-specific $b_0$ and $b_3$ estimates are set to 0.

::: {.panel-tabset}
#### Total barriers

In general, contentious aid doesn't really change at all as additional legal barriers are added. The slope of the line is 0.02 percentage points, with a credible interval that ranges between -0.2 and 0.25 percentage points. The effect is essentially zero.

```{r plot-cfx-range-total}
#| out-width: 80%
m_purpose_outcome_total$model %>% 
  epred_draws(newdata = datagrid(model = m_purpose_outcome_total$model,
                                 year_c = 0,
                                 barriers_total = seq(0, 10, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = barriers_total, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_continuous(breaks = seq(0, 10, by = 2)) +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Total barriers", y = "Predicted proportion of\ncontentious aid in the following year") +
  theme_donors()
```

```{r cfx-mfx-total}
mfx_purpose_cfx_multiple$total %>% 
  select(barriers_total, dydx, conf.low, conf.high)
```

```{r cfx-mfx-total-p-direction}
mfx_total_p_direction <- mfx_purpose_cfx_multiple$total %>% 
  posteriordraws() %>% 
  filter(barriers_total == 1) %>% 
  summarize(pd = sum(draw < 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-total}
#| out-width: 80%
mfx_purpose_cfx_multiple$total %>% 
  posteriordraws() %>% 
  filter(barriers_total %in% c(1, 7)) %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(barriers_total))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(2, 4, 6)]) +
  labs(x = "Conditional effect of total barriers on the\nproportion of contentious aid in the following year", y = NULL,
       subtitle = glue("P(ATE > 0) = {1 - pull(mfx_total_p_direction, pd_short)}"), fill = NULL) +
  theme_donors()
```

#### Advocacy

Contentious aid *increases* a little in response to restrictions on advocacy. The marginal effect when moving from 1 to 2 advocacy restrictions is half a percentage point, and the probability that it's greater than zero is 0.85.

```{r plot-cfx-range-advocacy}
#| out-width: 80%
m_purpose_outcome_advocacy$model %>% 
  epred_draws(newdata = datagrid(model = m_purpose_outcome_advocacy$model,
                                 year_c = 0,
                                 advocacy = seq(0, 2, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = advocacy, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_continuous(breaks = 0:2) +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Barriers to advocacy", y = "Predicted proportion of\ncontentious aid in the following year") +
  theme_donors()
```

```{r cfx-mfx-advocacy}
mfx_purpose_cfx_multiple$advocacy %>% 
  select(advocacy, dydx, conf.low, conf.high)
```

```{r cfx-mfx-advocacy-p-direction}
mfx_advocacy_p_direction <- mfx_purpose_cfx_multiple$advocacy %>% 
  posteriordraws() %>% 
  filter(advocacy == 1) %>% 
  summarize(pd = sum(draw > 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-advocacy}
#| out-width: 80%
mfx_purpose_cfx_multiple$advocacy %>% 
  posteriordraws() %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(advocacy))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(2, 4, 6)]) +
  labs(x = "Conditional effect of barriers to advocacy on the\nproportion of contentious aid in the following year", y = NULL,
       subtitle = glue("P(ATE > 0) = {pull(mfx_advocacy_p_direction, pd_short)}"), fill = NULL) +
  theme_donors()
```

#### Entry

Contentious aid *increases* a little in response to restrictions on entry. The marginal effect is 0.3 percentage points, and the probability that it's greater than zero is 0.89.

```{r plot-cfx-range-entry}
#| out-width: 80%
m_purpose_outcome_entry$model %>% 
  epred_draws(newdata = datagrid(model = m_purpose_outcome_entry$model,
                                 year_c = 0,
                                 entry = seq(0, 3, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = entry, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_continuous(breaks = 0:3) +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Barriers to entry", y = "Predicted proportion of\ncontentious aid in the following year") +
  theme_donors()
```

```{r cfx-mfx-entry}
mfx_purpose_cfx_multiple$entry %>% 
  select(entry, dydx, conf.low, conf.high)
```

```{r cfx-mfx-entry-p-direction}
mfx_entry_p_direction <- mfx_purpose_cfx_multiple$entry %>% 
  posteriordraws() %>% 
  filter(entry == 1) %>% 
  summarize(pd = sum(draw > 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-entry}
#| out-width: 80%
mfx_purpose_cfx_multiple$entry %>% 
  posteriordraws() %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(entry))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(2, 4, 6, 7)]) +
  labs(x = "Conditional effect of barriers to entry on the\nproportion of contentious aid in the following year", y = NULL,
       subtitle = glue("P(ATE > 0) = {pull(mfx_entry_p_direction, pd_short)}"), fill = NULL) +
  theme_donors()
```

#### Funding

Contentious aid *decreases* a little in response to restrictions on funding. The marginal effect is -0.3 percentage points, and the probability that it's less than 0 is 0.87.

```{r plot-cfx-range-funding}
#| out-width: 80%
m_purpose_outcome_funding$model %>% 
  epred_draws(newdata = datagrid(model = m_purpose_outcome_funding$model,
                                 year_c = 0,
                                 funding = seq(0, 4, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = funding, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_continuous(breaks = 0:4) +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Barriers to funding", y = "Predicted proportion of\ncontentious aid in the following year") +
  theme_donors()
```

```{r cfx-mfx-funding}
mfx_purpose_cfx_multiple$funding %>% 
  select(funding, dydx, conf.low, conf.high)
```

```{r cfx-mfx-funding-p-direction}
mfx_funding_p_direction <- mfx_purpose_cfx_multiple$funding %>% 
  posteriordraws() %>% 
  filter(funding == 1) %>% 
  summarize(pd = sum(draw < 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-funding}
#| out-width: 80%
mfx_purpose_cfx_multiple$funding %>% 
  posteriordraws() %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(funding))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(1, 2, 4, 6, 7)]) +
  labs(x = "Conditional effect of barriers to funding on the\nproportion of contentious aid in the following year", y = NULL,
       subtitle = glue("P(ATE < 0) = {pull(mfx_funding_p_direction, pd_short)}"), fill = NULL) +
  theme_donors()
```

#### Core civil society index

Contentious aid doesn't do much in response to changes in the de facto civil society environment. The official marginal effect is 0.01 percentage points (basically zero!) and the probability that it's greater than zero is only 0.64.

```{r plot-cfx-range-ccsi}
#| out-width: 80%
m_purpose_outcome_ccsi$model_50 %>% 
  epred_draws(newdata = datagrid(model = m_purpose_outcome_ccsi$model_50,
                                 year_c = 0,
                                 v2xcs_ccsi = seq(0, 1, 0.1)),
              re_formula = NA) %>% 
  ggplot(aes(x = v2xcs_ccsi, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_reverse() +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Core civil society index", y = "Predicted proportion of\ncontentious aid in the following year",
       caption = "**x-axis reversed**; lower values represent worse respect for civil society") +
  theme_donors() +
  theme(plot.caption = element_markdown())
```

```{r cfx-mfx-ccsi}
mfx_purpose_cfx_multiple$ccsi %>% 
  select(v2xcs_ccsi, dydx, conf.low, conf.high)
```

```{r cfx-mfx-ccsi-p-direction}
mfx_ccsi_p_direction <- mfx_purpose_cfx_multiple$ccsi %>% 
  posteriordraws() %>% 
  filter(v2xcs_ccsi == 0.5) %>% 
  summarize(pd = sum(draw < 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-ccsi}
#| out-width: 80%
mfx_purpose_cfx_multiple$ccsi %>% 
  posteriordraws() %>% 
  mutate(draw = -draw) %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(v2xcs_ccsi))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(1, 2, 4, 6, 7)]) +
  labs(x = "Conditional effect of worsening the\ncore civil society index on contentious aid in the following year", y = NULL,
       subtitle = glue("P(ATE < 0) = {1 - pull(mfx_ccsi_p_direction, pd_short)}"), fill = NULL) +
  theme_donors()
```

#### Civil society repression

However, contentious aid *increases* as repression decreases or improves a little (0.16 percentage points, with a 100% probability of being greater than zero). Or in reverse, as civil society gets worse, contentious aid *decreases* (following @Bush:2015). This is interesting since it's the opposite-ish for de jure restrictions—when barriers to advocacy and entry are enacted, contentious aid increases a little bit. But when the practical lived level of civil society repression increases, contentious aid drops. 

```{r plot-cfx-range-repress}
#| out-width: 80%
m_purpose_outcome_repress$model_50 %>% 
  epred_draws(newdata = datagrid(model = m_purpose_outcome_repress$model_50,
                                 year_c = 0,
                                 v2csreprss = seq(-4, 3, 0.25)),
              re_formula = NA)  %>% 
  ggplot(aes(x = v2csreprss, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_reverse(labels = label_number(style_negative = "minus")) +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Civil society repression", y = "Predicted proportion of\ncontentious aid in the following year",
       caption = "**x-axis reversed**; lower values represent greater civil society repression") +
  theme_donors() +
  theme(plot.caption = element_markdown())
```

```{r cfx-mfx-repress}
mfx_purpose_cfx_multiple$repress %>% 
  select(v2csreprss, dydx, conf.low, conf.high)
```

```{r cfx-mfx-repress-p-direction}
mfx_repress_p_direction <- mfx_purpose_cfx_multiple$repress %>% 
  posteriordraws() %>% 
  filter(v2csreprss == 0) %>% 
  summarize(pd = sum(draw < 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-repress}
#| out-width: 80%
mfx_purpose_cfx_multiple$repress %>% 
  posteriordraws() %>% 
  mutate(draw = -draw) %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(v2csreprss))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(1, 2, 4, 6, 7)]) +
  labs(x = "Conditional effect of worsening\ncivil society repression on contentious aid in the following year", y = NULL,
       subtitle = glue("P(ATE < 0) = {1 - pull(mfx_repress_p_direction, pd_short)}"), fill = NULL) +
  theme_donors()
```

:::


### Combined plots

#### Predictions

```{r build-cfx-predictions-combined}
ci_cols <- c("grey70", "grey45", "grey20")

p1 <- m_purpose_outcome_total$model %>% 
  epred_draws(newdata = datagrid(model = m_purpose_outcome_total$model,
                                 year_c = 0,
                                 barriers_total = seq(0, 10, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = barriers_total, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_continuous(breaks = seq(0, 10, by = 2)) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$PurpOr[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$PurpOr[c(1, 3, 5)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0.035, 0.085)) +
  facet_wrap(vars("Total barriers")) +
  theme_donors() + 
  theme(legend.margin = margin(l = 7.5, r = 7.5))

p2 <- m_purpose_outcome_advocacy$model %>% 
  epred_draws(newdata = datagrid(model = m_purpose_outcome_advocacy$model,
                                 year_c = 0,
                                 advocacy = seq(0, 2, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = advocacy, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_continuous(breaks = 0:2) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Teal[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Teal[c(1, 3, 5)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0.035, 0.085)) +
  facet_wrap(vars("Barriers to advocacy")) +
  theme_donors() + 
  theme(legend.margin = margin(l = 7.5, r = 7.5))

p3 <- m_purpose_outcome_entry$model %>% 
  epred_draws(newdata = datagrid(model = m_purpose_outcome_entry$model,
                                 year_c = 0,
                                 entry = seq(0, 3, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = entry, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_continuous(breaks = 0:3) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Emrld[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Emrld[c(1, 3, 5)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0.035, 0.085)) +
  facet_wrap(vars("Barriers to entry")) +
  theme_donors() + 
  theme(legend.margin = margin(l = 7.5, r = 7.5))

p4 <- m_purpose_outcome_funding$model %>% 
  epred_draws(newdata = datagrid(model = m_purpose_outcome_funding$model,
                                 year_c = 0,
                                 funding = seq(0, 4, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = funding, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_continuous(breaks = 0:4) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Peach[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Peach[c(1, 3, 5)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0.035, 0.085)) +
  facet_wrap(vars("Barriers to funding")) +
  theme_donors() + 
  theme(legend.margin = margin(l = 7.5, r = 7.5))
```

```{r plot-cfx-predictions-combined, fig.width=7, fig.height=5}
#| out-width: 90%
#| fig-cap: "The effect of de jure anti-NGO legal barriers on the predicted 
#|   proportion of contentious aid in a typical country"

# Put the shared y-axis label in a separate plot and add it to the combined plot
# https://stackoverflow.com/a/66778622/120898
p_lab <- ggplot() + 
  annotate(geom = "text", x = 1, y = 1, angle = 90, size = 3.3, fontface = "bold",
           label = "Predicted proportion of\ncontentious aid in the following year") +
  coord_cartesian(clip = "off") +
  theme_void()

(p_lab | 
    ((p1 | p2) / (p3 | p4) + 
       plot_layout(guides = "collect") + 
       plot_annotation(theme = theme(legend.position = "bottom")))) + 
  plot_layout(widths = c(0.05, 1))
```

```{r plot-cfx-predictions-defacto, fig.width=7, fig.height=3.6}
#| out-width: 90%
#| fig-cap: "The effect of the de facto civil society legal environment on the 
#|   predicted proportion of contentious aid in a typical country"
p1 <- m_purpose_outcome_ccsi$model_50 %>% 
  epred_draws(newdata = datagrid(model = m_purpose_outcome_ccsi$model_50,
                                 year_c = 0,
                                 v2xcs_ccsi = seq(0, 1, 0.1)),
              re_formula = NA) %>% 
  ggplot(aes(x = v2xcs_ccsi, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_reverse(breaks = seq(0, 1, by = 0.25)) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Sunset[4],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Sunset[c(1, 2, 3)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0.01, 0.05)) +
  facet_wrap(vars("Worsening core civil society index")) +
  theme_donors() +
  theme(legend.margin = margin(l = 7.5, r = 7.5))

p2 <- m_purpose_outcome_repress$model_50 %>% 
  epred_draws(newdata = datagrid(model = m_purpose_outcome_repress$model_50,
                                 year_c = 0,
                                 v2csreprss = seq(-4, 3, 0.25)),
              re_formula = NA) %>% 
  ggplot(aes(x = v2csreprss, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_reverse(labels = label_number(style_negative = "minus")) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Sunset[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Sunset[c(4, 5, 6)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):",
       caption = "**x-axis reversed**; lower values represent worse respect for and repression of civil society") +
  coord_cartesian(ylim = c(0.01, 0.05)) +
  facet_wrap(vars("Worsening civil society repression")) +
  theme_donors() +
  theme(legend.margin = margin(l = 7.5, r = 7.5),
        plot.caption = element_markdown())

p_lab <- ggplot() + 
  annotate(geom = "text", x = 1, y = 1, angle = 90, size = 3.3, fontface = "bold",
           label = "Predicted proportion of\ncontentious aid in the following year") +
  coord_cartesian(clip = "off") +
  theme_void()

(p_lab | 
    ((p1 | p2) + 
       plot_layout(guides = "collect") + 
       plot_annotation(theme = theme(legend.position = "bottom")))) + 
  plot_layout(widths = c(0.05, 1))
```


#### Conditional marginal effects

```{r calc-cfx-mfx-all}
mfx_total_stats <- mfx_purpose_cfx_single$total %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_advocacy_stats <- mfx_purpose_cfx_single$advocacy %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_entry_stats <- mfx_purpose_cfx_single$entry %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_funding_stats <- mfx_purpose_cfx_single$funding %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_ccsi_stats <- mfx_purpose_cfx_single$ccsi %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_repress_stats <- mfx_purpose_cfx_single$repress %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r build-cfx-mfx-combined}
p1 <- mfx_purpose_cfx_single$total %>% 
  posteriordraws() %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$PurpOr[6], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE > 0) = {1 - pull(mfx_total_stats, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$PurpOr[4], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("One additional barrier of any type")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p2 <- mfx_purpose_cfx_single$advocacy %>% 
  posteriordraws() %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$Teal[4], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE > 0) = {1 - pull(mfx_advocacy_stats, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Teal[6], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("One additional barrier to advocacy")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p3 <- mfx_purpose_cfx_single$entry %>% 
  posteriordraws() %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$Emrld[4], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE > 0) = {1 - pull(mfx_entry_stats, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Emrld[6], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("One additional barrier to entry")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p4 <- mfx_purpose_cfx_single$funding %>% 
  posteriordraws() %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$Peach[6], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE < 0) = {pull(mfx_funding_stats, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Peach[4], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("One additional barrier to funding")) +
  theme_donors() +
  theme(axis.text.y = element_blank())
```

```{r plot-cfx-mfx-combined, fig.width=7, fig.height=5.2}
#| out-width: 90%
#| fig-cap: "The effect of one additional de jure anti-NGO legal barrier on  
#|   the predicted proportion of contentious aid in a typical country"
p_lab <- ggplot() + 
  annotate(geom = "text", x = 1, y = 1, size = 3.3, fontface = "bold",
           label = "Conditional effect of treatment on proportion\nof contentious aid in the following year") +
  coord_cartesian(clip = "off") +
  theme_void()

(((p1 | p2) / (p3 | p4)) / p_lab) + 
  plot_layout(heights = c(1, 1, 0.1)) +
  plot_annotation(caption = "Point shows median value;\nthick bar = 80% credible interval; thin bar = 95% credible interval")
```

```{r plot-cfx-mfx-defacto, fig.width=7, fig.height=3.6}
#| out-width: 90%
#| fig-cap: "The effect of changes in the de facto civil society legal 
#|   environment on the predicted proportion of contentious aid in a typical 
#|   country"
p1 <- mfx_purpose_cfx_single$ccsi %>% 
  posteriordraws() %>% 
  mutate(draw = -draw / 10) %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$Sunset[4], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE < 0) = {1 - pull(mfx_ccsi_stats, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Sunset[3], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("A 0.1 unit decrease (worsening) in\nthe core civil society index")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p2 <- mfx_purpose_cfx_single$repress %>% 
  posteriordraws() %>% 
  mutate(draw = -draw) %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x > 0)),
               fill = clrs$Sunset[6], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE < 0) = {1 - pull(mfx_repress_stats, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Sunset[3], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("A 1 unit decrease (worsening) in\nthe civil society repression score")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p_lab <- ggplot() + 
  annotate(geom = "text", x = 1, y = 1, size = 3.3, fontface = "bold",
           label = "Conditional effect of treatment on proportion\nof contentious aid in the following year") +
  coord_cartesian(clip = "off") +
  theme_void()

((p1 | p2) / p_lab) + 
  plot_layout(heights = c(1, 0.15)) +
  plot_annotation(caption = "Point shows median value;\nthick bar = 80% credible interval; thin bar = 95% credible interval")
```


#### Table

With H~1~ we had to convert the dollar-scale treatment effects into percent changes to make them more interpretable, since we were working with millions of dollars. With this outcome, though, we're just working with a 0–100% range, so we can stick with percentage point-scale effects. 

```{r build-cfx-mfx-results-table}
signif_pp <- label_number(accuracy = 0.01, scale = 100, suffix = " pp.",
                          style_negative = "minus")
signif_no_pp <- label_number(accuracy = 0.01, scale = 100,
                             style_negative = "minus")

mfx_lookup <- tribble(
  ~term, ~Treatment,
  "barriers_total", "One additional barrier of any type",
  "advocacy", "One additional barrier to advocacy",
  "entry", "One additional barrier to entry",
  "funding", "One additional barrier to funding",
  "v2xcs_ccsi", "A 0.1 unit decrease in the core civil society index (i.e. worse environment)",
  "v2csreprss", "A 1 unit decrease in the civil society repression score (i.e. more repression)"
) %>% 
  mutate(Treatment = fct_inorder(Treatment))

mfx_all_posteriors <- bind_rows(
  posteriordraws(mfx_purpose_cfx_single$total), 
  posteriordraws(mfx_purpose_cfx_single$advocacy), 
  posteriordraws(mfx_purpose_cfx_single$entry), 
  posteriordraws(mfx_purpose_cfx_single$funding),
  (posteriordraws(mfx_purpose_cfx_single$ccsi) %>% mutate(draw = draw / 10)),
  posteriordraws(mfx_purpose_cfx_single$repress)) %>% 
  mutate(draw = ifelse(term %in% c("v2xcs_ccsi", "v2csreprss"), -draw, draw),
         dydx = ifelse(term %in% c("v2xcs_ccsi", "v2csreprss"), -dydx, dydx),
         conf.low_real = ifelse(term %in% c("v2xcs_ccsi", "v2csreprss"), -conf.high, conf.low),
         conf.high_real = ifelse(term %in% c("v2xcs_ccsi", "v2csreprss"), -conf.low, conf.high),
         conf.low = conf.low_real, conf.high = conf.high_real)

mfx_p_direction <- mfx_all_posteriors %>% 
  group_by(term) %>% 
  summarize(pd_lt = round(sum(draw < 0) / n(), 2),
            pd_gt = round(sum(draw > 0) / n(), 2))

mfx_medians <- mfx_all_posteriors %>% 
  group_by(term) %>% 
  median_hdci(draw) %>%
  left_join(mfx_p_direction, by = "term") %>% 
  mutate(direction = case_when(
    draw > 0 ~ "more contentious aid in the next year",
    draw < 0 ~ "less contentious aid in the next year"
  )) %>% 
  mutate(pd = case_when(
    draw > 0 ~ pd_gt,
    draw < 0 ~ pd_lt
  )) %>% 
  mutate(pd_nice = label_percent(accuracy = 1)(pd)) %>% 
  mutate(across(c(draw, .upper), ~signif_pp(.))) %>% 
  mutate(.lower = signif_no_pp(.lower)) %>% 
  mutate(interval = glue("[{.lower}, {.upper}]")) %>% 
  mutate(draw_nice = glue("{draw}\n{interval}")) %>% 
  left_join(mfx_lookup, by = "term")

mfx_medians_with_plots <- mfx_medians %>% 
  group_by(term) %>% 
  nest() %>% 
  mutate(sparkplot = map(data, ~spark_bar(.x))) %>% 
  mutate(sparkname = glue("sparkplots/contentiousness_bar_{term}")) %>% 
  mutate(saved_plot = map2(sparkplot, sparkname, ~save_sparks(.x, .y)))

mfx_median_clean <- mfx_medians_with_plots %>% 
  ungroup() %>% 
  select(-sparkplot) %>% 
  unnest_wider(saved_plot) %>% 
  unnest(data) %>% 
  arrange(Treatment)
```

```{r cfx-mfx-results-table}
#| column: screen-inset-right
tbl_notes <- c("The probability denotes the percentage of the posterior distribution that falls above or below 0.",
               "Reported values are the median posterior marginal effect of each treatment variable on the outcome, multiplied by 100 to show percentage point changes; 95% highest posterior density intervals (HPDI) shown in brackets.")

mfx_median_clean %>% 
  mutate(Probability = "") %>% 
  # mutate(across(c(draw.nice, pct_change.nice), ~linebreak(., align = "c"))) %>%  # For LaTeX
  mutate(draw_nice = str_replace(draw_nice, "\\n", "<br>")) %>% 
  select(Treatment, direction, Probability, draw_nice) %>% 
  set_names(c(paste0("Probability", footnote_marker_symbol(1)),
              "Countries that add…", 
              "…receive…", 
              paste0("Median", footnote_marker_symbol(2)))) %>% 
  kbl(align = c("l", "l", "l", "c"), escape = FALSE) %>% 
  kable_styling(htmltable_class = "table table-sm table-borderless") %>% 
  pack_rows("De jure legislation", 1, 4, indent = FALSE) %>% 
  pack_rows("De facto enforcement", 5, 6, indent = FALSE) %>% 
  column_spec(1, width = "34%") %>% 
  column_spec(2, width = "34%") %>% 
  column_spec(3, image = mfx_median_clean$png, width = "14%") %>% 
  column_spec(4, width = "18%") %>% 
  footnote(symbol = tbl_notes, footnote_as_chunk = FALSE)
```

### Within- and between-country variability (φ and σs)

```{r extract-sigmas-total, include=FALSE, warning=FALSE}
zi_coefs <- m_purpose_outcome_total$model %>% 
  tidy(effects = "fixed") %>% 
  mutate(term = janitor::make_clean_names(term)) %>% 
  mutate(across(c(estimate, conf.low, conf.high), list(exp = ~exp(.)))) %>% 
  split(~term)

sigmas_zi <- m_purpose_outcome_total$model %>% 
  tidy(parameters = c("sd_*", "phi")) %>% 
  select(-component) %>% 
  mutate(term = janitor::make_clean_names(term)) %>% 
  split(~term)

zimuint <- plogis(zi_coefs$intercept$estimate)
ziphi <- exp(sigmas_zi$phi$estimate)
```

The $\phi$ and $\sigma$ terms are roughly the same across all these different models, so we'll just show the results from the total barriers model here. We have three uncertainty-related terms to work with:

- $\phi_y$ (`phi`): the precision or variance of aid contentiousness within countries. On the log scale, it's `r round(sigmas_zi$phi$estimate, 2)`, which is `r round(exp(sigmas_zi$phi$estimate), 0)` when unlogged or exponentiated, which is incredibly precise. That gives us a posterior distribution of the non-zero-inflated part of the model of $\operatorname{Beta}(`r zimuint`, `r round(ziphi, 0)`)$ which looks like this, very narrowly focused around the baseline average 2000 proportion:

```{r plot-zi-phi, warning=FALSE, indent="  "}
#| out-width: 70%
beta_params <- m_purpose_outcome_total$model %>% 
  tidy(parameters = c("b_(Intercept)", "phi"))

beta_mu <- beta_params %>% 
  filter(term == "b_(Intercept)") %>% 
  pull(estimate)

beta_phi <- beta_params %>% 
  filter(term == "phi") %>% 
  pull(estimate)

ggplot() +
  stat_function(geom = "area", fill = clrs$Prism[7],
                fun = ~dprop(., mean = plogis(beta_mu), size = exp(beta_phi))) +
  scale_x_continuous(labels = label_percent(), limits = c(0.067, 0.07)) +
  labs(title = "Distribution of non-zero-inflated contentious aid in 2000",
       subtitle = glue::glue("Beta(µ = plogis({round(beta_mu, 2)}), φ = exp({round(beta_phi, 2)})) or Beta(µ = {round(plogis(beta_mu), 3)}, φ = {round(exp(beta_phi), 0)})")) +
  theme_donors()
```

- $\sigma_0$ (`sd__(Intercept)` for the `gwcode` group): the variability between countries' baseline averages, or the variability around the $b_{0_j}$ offsets. Here it's `r round(sigmas_zi$sd_gwcode_intercept$estimate, 2)`, which means that across or between countries, the proportion of contentious aid varies by 0.5ish logit units.

- $\sigma_3$ (`sd__year_c` for the `gwcode` group): the variability between countries' year effects, or the variability around the $b_{3_j}$ offsets. Here it's `r round(sigmas_zi$sd_gwcode_year_c$estimate, 2)`, which means that average year effects vary by 0.04 logit units across or between countries.

```{r show-sigmas-zi, warning=FALSE}
#| code-fold: show
m_purpose_outcome_total$model %>% 
  tidy(parameters = c("sd_*", "phi")) %>% 
  select(-component)
```


### Full results table

Again, this is less important since we don't care about individual coefficients and instead care about conditional effects, but for the sake of full transparency (and to placate future reviewers), here's a table of all the results:

```{r tbl-h2-outcome, warning=FALSE}
#| tbl-cap: Results from all outcome models
models_tbl_h2_outcome_dejure <- models_tbl_h2_outcome_dejure %>% 
  set_names(1:length(.))

notes <- c(
  "Posterior medians; 95% credible intervals (HDPI) in brackets.", 
  "Total \\(R^2\\) considers the variance of both population and group effects;", 
  "marginal \\(R^2\\) only takes population effects into account"
)

modelsummary(models_tbl_h2_outcome_dejure,
             estimate = "{estimate}",
             statistic = "[{conf.low}, {conf.high}]",
             add_rows = outcome_rows,
             coef_map = coefs_outcome,
             gof_map = gofs,
             output = "kableExtra",
             fmt =  list(estimate = 2, conf.low = 2, conf.high = 2)) %>% 
  row_spec(1, bold = TRUE) %>% 
  kable_styling(htmltable_class = "table-sm light-border") %>% 
  footnote(general = notes, footnote_as_chunk = TRUE)
```
