---
title: "H~3~: Effect of anti-NGO crackdown on aid recipients"
format:
  html:
    code-fold: true
    toc-depth: 6
    knitr:
      opts_chunk:
        out.width: "80%"
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(digits = 3, width = 120,
        dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(brms)
library(tidybayes)
library(broom)
library(broom.mixed)
library(modelsummary)
library(marginaleffects)
library(patchwork)
library(scales)
library(ggdist)
library(ggtext)
library(ggh4x)
library(extraDistr)
library(kableExtra)
library(glue)
library(here)

tar_config_set(store = here::here('_targets'),
               script = here::here('_targets.R'))

set.seed(1234)

# Load stuff from targets
# Plotting functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(tbl_functions), .GlobalEnv))
set_annotation_fonts()

# Tell bayesplot to use the sunset palette for things like pp_check()
bayesplot::color_scheme_set(clrs$Sunset[2:7])

# Data
df_country_aid <- tar_read(country_aid_final) %>% 
  filter(year > 2000 & year < 2013)
df_country_aid_laws <- filter(df_country_aid, laws)

# Treatment models
tar_load(c(m_recip_treatment_total_dom, m_recip_treatment_advocacy_dom, 
           m_recip_treatment_entry_dom, m_recip_treatment_funding_dom, 
           m_recip_treatment_ccsi_dom, m_recip_treatment_repress_dom))
tar_load(c(m_recip_treatment_total_foreign, m_recip_treatment_advocacy_foreign, 
           m_recip_treatment_entry_foreign, m_recip_treatment_funding_foreign, 
           m_recip_treatment_ccsi_foreign, m_recip_treatment_repress_foreign))

# IPTW data
tar_load(c(df_recip_iptw_total_dom, df_recip_iptw_advocacy_dom, 
           df_recip_iptw_entry_dom, df_recip_iptw_funding_dom,
           df_recip_iptw_ccsi_dom, df_recip_iptw_repress_dom))
tar_load(c(df_recip_iptw_total_foreign, df_recip_iptw_advocacy_foreign, 
           df_recip_iptw_entry_foreign, df_recip_iptw_funding_foreign,
           df_recip_iptw_ccsi_foreign, df_recip_iptw_repress_foreign))

# Outcome models
tar_load(c(m_recip_outcome_total_dom, m_recip_outcome_advocacy_dom, 
           m_recip_outcome_entry_dom, m_recip_outcome_funding_dom,
           m_recip_outcome_ccsi_dom, m_recip_outcome_repress_dom))
tar_load(c(m_recip_outcome_total_foreign, m_recip_outcome_advocacy_foreign, 
           m_recip_outcome_entry_foreign, m_recip_outcome_funding_foreign,
           m_recip_outcome_ccsi_foreign, m_recip_outcome_repress_foreign))

# Marginal/conditional effects
tar_load(c(mfx_recip_cfx_multiple_dom, mfx_recip_cfx_single_dom,
           mfx_recip_cfx_multiple_foreign, mfx_recip_cfx_single_foreign))

# Results tables
tar_load(c(models_tbl_h3_treatment_num_dom, models_tbl_h3_treatment_denom_dom))
tar_load(c(models_tbl_h3_treatment_num_foreign, models_tbl_h3_treatment_denom_foreign))
tar_load(c(models_tbl_h3_outcome_dejure_dom, models_tbl_h3_outcome_defacto_dom))
tar_load(c(models_tbl_h3_outcome_dejure_foreign, models_tbl_h3_outcome_defacto_foreign))
```

```{r modelsummary-settings}
invisible(list2env(tar_read(modelsummary_functions), .GlobalEnv))

treatment_names <- c("Treatment", "Total barriers (t)", "Barriers to advocacy (t)", 
                     "Barriers to entry (t)", "Barriers to funding (t)", "CCSI (t)",
                     "CS repression (t)")
treatment_rows <- as.data.frame(t(treatment_names))
attr(treatment_rows, "position") <- 1

outcome_names <- c("Treatment", "Total barriers (t)", "Barriers to advocacy (t)", 
                   "Barriers to entry (t)", "Barriers to funding (t)")
outcome_rows <- as.data.frame(t(outcome_names))
attr(outcome_rows, "position") <- 1
```

# Weight models

## General idea

See the ["Weight models—General idea" section from the total aid page](models_total-aid.qmd#general-idea) for an explanation of the intuition behind how to create these stabilized weights.

## Actual models

We identify our time-varying and time-invariant confounders based on [our causal model and *do*-calculus logic](causal-model.qmd#final-variables-to-use), and we deal with the panel structure of the data by including random intercepts for country, and both a population-level trend and random slopes for year. We use [generic weakly informative priors](https://mc-stan.org/users/documentation/case-studies/weakly_informative_shapes.html) for our model parameters.

### Numerator

Our numerator models look like this (but with the actual treatment variable replacing `treatment`, like `barriers_total`, `advocacy`, and so on):

```{r fake-numerator, eval=FALSE}
#| code-fold: show
bf(treatment ~ treatment_lag1 + treatment_lag2_cumsum + (1 | gwcode))
```

Or more formally:

$$
\begin{aligned}
\text{Treatment}_{it_j} &\sim \mathcal{N}(\mu_{it_j}, \sigma_y) \\
\mu_{it_j} &= (\beta_0 + b_{0_j}) + \beta_1 \text{Treatment}_{i, t-1_j} + \textstyle{\sum_{\tau = (t-2)}^{t}} \text{Treatment}_{i\tau} \\
b_{0_j} &\sim \mathcal{N}(0, \sigma_0) \\
\\
\beta_0, \beta_1 &\sim \operatorname{Student~\textit{t}\,}(\nu = 3, \mu = 0, \sigma = 1.5) \\
\sigma_y, \sigma_0 &\sim \operatorname{Exponential}(1)
\end{aligned}
$$

### Denominator

Our denominator models look like this (but again with the actual treatment variable replacing `treatment`):

::: {.panel-tabset}
#### Domestic NGO recipients

```{r fake-denominator-dom, eval=FALSE}
#| code-fold: show
bf(treatment ~ treatment_lag1 + treatment_lag2_cumsum + 
     # Lagged outcome
     prop_ngo_dom_lag1 +
     # Human rights and politics
     v2x_polyarchy + v2x_corr + v2x_rule + v2x_civlib + v2x_clphy + v2x_clpriv +
     # Economics and development
     gdpcap_log_z + un_trade_pct_gdp + v2peedueq + v2pehealth + e_peinfmor +
     # Conflict and disasters
     internal_conflict_past_5 + natural_dis_count +
     # Time and country effects
     year_c + (1 + year_c | gwcode))
```

Or more formally:

$$
\begin{aligned}
\text{Treatment}_{it_j} \sim&\ \mathcal{N}(\mu_{it_j}, \sigma_y) \\
\mu_{it_j} =&\ (\beta_0 + b_{0_j}) + \beta_1\, \text{Treatment}_{i, t-1_j} + \beta_2\, \textstyle{\sum_{\tau = (t-2)}^{t}} \text{Treatment}_{i\tau} + \\
&\ \beta_3\, \text{Proportion of USAID aid to domestic NGOs}_{i,t-1_j} + \\
&\ \beta_{4 \ldots 9}\, \text{Human rights \& politics}_{it_j} + \\
&\ \beta_{10 \ldots 14}\, \text{Economics \& development} + \beta_{15, 16}\, \text{Conflict \& disasters}_{it_j} + \\
&\ (\beta_{17} + b_{17_j})\, \text{Year}_{it_j} \\
\left(
  \begin{array}{c} 
  b_{0_j} \\
  b_{17_j}
  \end{array}
\right) 
\sim&\ \text{MV}\,\mathcal{N}
\left[
  \left(
    \begin{array}{c}
    0 \\
    0 \\
    \end{array}
  \right)
  , \,
  \left(
  \begin{array}{cc}
     \sigma^2_{0} & \rho_{0, 17}\, \sigma_{0} \sigma_{17} \\ 
     \cdots & \sigma^2_{17}
  \end{array}
\right)
\right] \\
\\
\beta_0 \ldots \beta_{17} \sim&\ \operatorname{Student~\textit{t}\,}(\nu = 3, \mu = 0, \sigma = 1.5) \\
\sigma_y, \sigma_0, \sigma_{17} \sim&\ \operatorname{Exponential}(1) \\
\rho \sim&\ \operatorname{LKJ}(2)
\end{aligned}
$$

#### Foreign NGO recipients

```{r fake-denominator-foreign, eval=FALSE}
#| code-fold: show
bf(treatment ~ treatment_lag1 + treatment_lag2_cumsum + 
     # Lagged outcome
     prop_ngo_foreign_lag1 +
     # Human rights and politics
     v2x_polyarchy + v2x_corr + v2x_rule + v2x_civlib + v2x_clphy + v2x_clpriv +
     # Economics and development
     gdpcap_log_z + un_trade_pct_gdp + v2peedueq + v2pehealth + e_peinfmor +
     # Conflict and disasters
     internal_conflict_past_5 + natural_dis_count +
     # Time and country effects
     year_c + (1 + year_c | gwcode))
```

Or more formally:

$$
\begin{aligned}
\text{Treatment}_{it_j} \sim&\ \mathcal{N}(\mu_{it_j}, \sigma_y) \\
\mu_{it_j} =&\ (\beta_0 + b_{0_j}) + \beta_1\, \text{Treatment}_{i, t-1_j} + \beta_2\, \textstyle{\sum_{\tau = (t-2)}^{t}} \text{Treatment}_{i\tau} + \\
&\ \beta_3\, \text{Proportion of USAID aid to foreign NGOs}_{i,t-1_j} + \\
&\ \beta_{4 \ldots 9}\, \text{Human rights \& politics}_{it_j} + \\
&\ \beta_{10 \ldots 14}\, \text{Economics \& development} + \beta_{15, 16}\, \text{Conflict \& disasters}_{it_j} + \\
&\ (\beta_{17} + b_{17_j})\, \text{Year}_{it_j} \\
\left(
  \begin{array}{c} 
  b_{0_j} \\
  b_{17_j}
  \end{array}
\right) 
\sim&\ \text{MV}\,\mathcal{N}
\left[
  \left(
    \begin{array}{c}
    0 \\
    0 \\
    \end{array}
  \right)
  , \,
  \left(
  \begin{array}{cc}
     \sigma^2_{0} & \rho_{0, 17}\, \sigma_{0} \sigma_{17} \\ 
     \cdots & \sigma^2_{17}
  \end{array}
\right)
\right] \\
\\
\beta_0 \ldots \beta_{17} \sim&\ \operatorname{Student~\textit{t}\,}(\nu = 3, \mu = 0, \sigma = 1.5) \\
\sigma_y, \sigma_0, \sigma_{17} \sim&\ \operatorname{Exponential}(1) \\
\rho \sim&\ \operatorname{LKJ}(2)
\end{aligned}
$$

:::


## MCMC diagnostics

Once again, we verify that everything converged by checking diagnostics for the weight models for the total barriers treatment for domestic NGO recipients. All the other models look basically the same as this—everything is once again fine.

### Numerator

::: {.panel-tabset}

#### Trace plots

```{r plot-num-trace, warning=FALSE}
#| out-width: 80%
m_recip_treatment_total_dom$model_num %>% 
  gather_draws(`^b_.*|^sd_.*|^sigma`, regex = TRUE) %>% 
  ggplot(aes(x = .iteration, y = .value, color = factor(.chain))) +
  geom_line(linewidth = 0.1) +
  scale_color_manual(values = clrs$Sunset[3:6]) +
  facet_wrap(vars(.variable), scales = "free_y") +
  theme_donors()
```

#### Trank plots

```{r plot-num-trank, warning=FALSE}
#| out-width: 80%
m_recip_treatment_total_dom$model_num %>% 
  gather_draws(`^b_.*|^sd_.*|^sigma`, regex = TRUE) %>% 
  group_by(.variable) %>% 
  mutate(draw_rank = rank(.value)) %>% 
  ggplot(aes(x = draw_rank, color = factor(.chain))) +
  stat_bin(geom = "step", binwidth = 500, position = position_identity(), boundary = 0) +
  scale_color_manual(values = clrs$Sunset[3:6]) +
  facet_wrap(vars(.variable), scales = "free_y") +
  theme_donors() +
  theme(axis.text.y = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank())
```

#### Posterior predictive check

```{r plot-num-ppcheck}
#| out-width: 80%
withr::with_seed(1234, {
  pp_check(m_recip_treatment_total_dom$model_num, ndraws = 20) +
    labs(x = "Total NGO barriers",
         title = "Numerator model") +
    theme_donors()
})
```

:::

### Denominator

::: {.panel-tabset}

#### Trace plots

```{r plot-denom-trace, warning=FALSE, fig.width=10, fig.height=7}
#| out-width: 100%
m_recip_treatment_total_dom$model_denom %>% 
  gather_draws(`^b_.*|^sd_.*|^cor_.*|^sigma`, regex = TRUE) %>% 
  ggplot(aes(x = .iteration, y = .value, color = factor(.chain))) +
  geom_line(linewidth = 0.1) +
  scale_color_manual(values = clrs$Sunset[3:6]) +
  facet_wrap(vars(.variable), scales = "free_y") +
  theme_donors()
```

#### Trank plots

```{r plot-denom-trank, warning=FALSE, fig.width=10, fig.height=7}
#| out-width: 100%
m_recip_treatment_total_dom$model_denom %>% 
  gather_draws(`^b_.*|^sd_.*|^cor_.*|^sigma`, regex = TRUE) %>% 
  group_by(.variable) %>% 
  mutate(draw_rank = rank(.value)) %>% 
  ggplot(aes(x = draw_rank, color = factor(.chain))) +
  stat_bin(geom = "step", binwidth = 500, position = position_identity(), boundary = 0) +
  scale_color_manual(values = clrs$Sunset[3:6]) +
  facet_wrap(vars(.variable), scales = "free_y") +
  theme_donors() +
  theme(axis.text.y = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank())
```

#### Posterior predictive check

```{r plot-denom-ppcheck}
#| out-width: 80%
withr::with_seed(1234, {
  pp_check(m_recip_treatment_total_dom$model_denom, ndraws = 20) +
    labs(x = "Total NGO barriers",
         title = "Denominator model") +
    theme_donors()
})
```

:::


## Check weights

As always, IPTWs should generally have a mean of 1 and shouldn't be too incredibly high.

:::: {.panel-tabset}

### Total barriers

::: {.panel-tabset}
#### % of aid to domestic NGO recipients

The max weight here is `r round(max(df_recip_iptw_total_dom$iptw), 0)`, but once again only a few observations have weights that high. The average is `r round(mean(df_recip_iptw_total_dom$iptw), 2)` and the median is `r round(median(df_recip_iptw_total_dom$iptw), 2)`, which are both essentially 1. Lovely.

```{r iptws-total-recip-dom}
#| code-fold: show
summary(df_recip_iptw_total_dom$iptw)
```

```{r plot-iptws-total-recip-dom}
df_recip_iptw_total_dom %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(binwidth = 0.5, boundary = 0) +
  theme_donors()
```

#### % of aid to foreign NGO recipients

Same here. The max weight is `r round(max(df_recip_iptw_total_foreign$iptw), 0)`, with an average of `r round(mean(df_recip_iptw_total_foreign$iptw), 2)` and a median of `r round(median(df_recip_iptw_total_foreign$iptw), 2)`, which are both essentially 1, so we're still good.

```{r iptws-total-recip-foreign}
#| code-fold: show
summary(df_recip_iptw_total_foreign$iptw)
```

```{r plot-iptws-total-recip-foreign}
df_recip_iptw_total_foreign %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(binwidth = 0.5, boundary = 0) +
  theme_donors()
```

:::

### Advocacy

::: {.panel-tabset}
#### % of aid to domestic NGO recipients

The max weight here is `r round(max(df_recip_iptw_advocacy_dom$iptw), 0)` which is lovely. The average is `r round(mean(df_recip_iptw_advocacy_dom$iptw), 2)`, so we're good.

```{r iptws-advocacy-dom}
#| code-fold: show
summary(df_recip_iptw_advocacy_dom$iptw)
```

```{r plot-iptws-advocacy-dom}
df_recip_iptw_advocacy_dom %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(binwidth = 0.5, boundary = 0) +
  theme_donors()
```

#### % of aid to foreign NGO recipients

The max weight here is `r round(max(df_recip_iptw_advocacy_foreign$iptw), 0)` and the average is `r round(mean(df_recip_iptw_advocacy_foreign$iptw), 2)`, so we're good.

```{r iptws-advocacy-foreign}
#| code-fold: show
summary(df_recip_iptw_advocacy_foreign$iptw)
```

```{r plot-iptws-advocacy-foreign}
df_recip_iptw_advocacy_foreign %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(binwidth = 0.5, boundary = 0) +
  theme_donors()
```

:::

### Entry

::: {.panel-tabset}
#### % of aid to domestic NGO recipients

The max weight here is `r round(max(df_recip_iptw_entry_dom$iptw), 0)` which is grand. The average is `r round(mean(df_recip_iptw_entry_dom$iptw), 2)`, so we're once again good.

```{r iptws-entry-dom}
#| code-fold: show
summary(df_recip_iptw_entry_dom$iptw)
```

```{r plot-iptws-entry-dom}
df_recip_iptw_entry_dom %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(binwidth = 0.5, boundary = 0) +
  theme_donors()
```

#### % of aid to foreign NGO recipients

The max weight here is `r round(max(df_recip_iptw_entry_foreign$iptw), 0)`and the average is `r round(mean(df_recip_iptw_entry_foreign$iptw), 2)`. Yay.

```{r iptws-entry-foreign}
#| code-fold: show
summary(df_recip_iptw_entry_foreign$iptw)
```

```{r plot-iptws-entry-foreign}
df_recip_iptw_entry_foreign %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(binwidth = 0.5, boundary = 0) +
  theme_donors()
```

:::

### Funding

::: {.panel-tabset}
#### % of aid to domestic NGO recipients

The max weight is `r round(max(df_recip_iptw_funding_dom$iptw), 0)` which is fine, and the average is `r round(mean(df_recip_iptw_funding_dom$iptw), 2)`, so all is well.

```{r iptws-funding-dom}
#| code-fold: show
summary(df_recip_iptw_funding_dom$iptw)
```

```{r plot-iptws-funding-dom}
df_recip_iptw_funding_dom %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(binwidth = 0.5, boundary = 0) +
  theme_donors()
```

#### % of aid to foreign NGO recipients

The max weight here is `r round(max(df_recip_iptw_funding_foreign$iptw), 0)` with an average of `r round(mean(df_recip_iptw_funding_foreign$iptw), 2)`, so all is still well.

```{r iptws-funding-foreign}
#| code-fold: show
summary(df_recip_iptw_funding_foreign$iptw)
```

```{r plot-iptws-funding-foreign}
df_recip_iptw_funding_foreign %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(binwidth = 0.5, boundary = 0) +
  theme_donors()
```

:::

### Core civil society index

::: {.panel-tabset}
#### % of aid to domestic NGO recipients

lol, as with the other hypotheses, these once again blow up. The max weight is `r label_comma()(max(df_recip_iptw_ccsi_dom$iptw))`.

```{r iptws-ccsi-dom}
#| code-fold: show
summary(df_recip_iptw_ccsi_dom$iptw)
```

There aren't a lot of observations with weights that high though. Check out the counts of rows with weights greater than 50 and greater than 500—only 100ish:

```{r show-threshold-counts-iptws-ccsi-dom}
#| code-fold: show
df_recip_iptw_ccsi_dom %>% count(iptw >= 50)
df_recip_iptw_ccsi_dom %>% count(iptw >= 500)
```

We truncate these weights at 50.

```{r plot-iptws-ccsi-dom}
plot_iptw_ccsi_dom <- bind_rows(
  df_recip_iptw_ccsi_dom %>% mutate(threshold = 50, iptw = ifelse(iptw > threshold, threshold, iptw)),
  df_recip_iptw_ccsi_dom %>% mutate(threshold = 500, iptw = ifelse(iptw > threshold, threshold, iptw))
) %>% 
  mutate(threshold = paste0("Truncated at ", threshold),
         threshold = fct_inorder(threshold))

plot_iptw_ccsi_dom %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(bins = 50, boundary = 0) +
  facet_wrap(vars(threshold), scales = "free_x") +
  theme_donors()
```

#### % of aid to foreign NGO recipients

Same here—these blow up in a comically huge way.

```{r iptws-ccsi-foreign}
#| code-fold: show
summary(df_recip_iptw_ccsi_foreign$iptw)
```

We also truncate these weights at 50.

```{r plot-iptws-ccsi-foreign}
plot_iptw_ccsi_foreign <- df_recip_iptw_ccsi_foreign %>% 
  mutate(threshold = 50, iptw = ifelse(iptw > threshold, threshold, iptw)) %>% 
  mutate(threshold = paste0("Truncated at ", threshold),
         threshold = fct_inorder(threshold))

plot_iptw_ccsi_foreign %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(bins = 50, boundary = 0) +
  facet_wrap(vars(threshold), scales = "free_x") +
  theme_donors()
```

:::

### Civil society repression

::: {.panel-tabset}
#### % of aid to domestic NGO recipients

These weights are also horrendous, with a maximum weight of `r label_comma()(max(df_recip_iptw_repress_dom$iptw))`.

```{r iptws-csrepress-dom}
#| code-fold: show
summary(df_recip_iptw_repress_dom$iptw)
```

As with the core civil society index, there aren't a lot of observations with weights that high:

```{r show-threshold-counts-iptws-csrepress-dom}
#| code-fold: show
df_recip_iptw_repress_dom %>% count(iptw >= 50)
df_recip_iptw_repress_dom %>% count(iptw >= 500)
```

So we truncate these weights at 50 again. Since the results from the core civil society models are basically the same when truncating at 500, we only use a truncation point of 50 here.

```{r plot-iptws-csrepress-dom}
df_recip_iptw_ccsi_dom %>% 
  mutate(threshold = 50, iptw = ifelse(iptw > threshold, threshold, iptw)) %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(bins = 50, boundary = 0) +
  theme_donors()
```

#### % of aid to foreign NGO recipients

Once again, lolz.

```{r iptws-csrepress-foreign}
#| code-fold: show
summary(df_recip_iptw_repress_foreign$iptw)
```

We also truncate these weights at 50.

```{r plot-iptws-csrepress-foreign}
plot_iptw_repress_foreign <- df_recip_iptw_repress_foreign %>% 
  mutate(threshold = 50, iptw = ifelse(iptw > threshold, threshold, iptw)) %>% 
  mutate(threshold = paste0("Truncated at ", threshold),
         threshold = fct_inorder(threshold))

plot_iptw_repress_foreign %>% 
  ggplot(aes(x = iptw)) +
  geom_histogram(bins = 50, boundary = 0) +
  facet_wrap(vars(threshold), scales = "free_x") +
  theme_donors()
```

:::

::::

## Results

These are less important since we just use these treatment models to generate weights *and* because interpreting each coefficient when trying to isolate causal effects is unimportant [@WestreichGreenland:2013; @KeeleStevensonElwert:2020].

:::: {.panel-tabset}

### % of aid to domestic NGO recipients

::: {.panel-tabset}

#### Numerator

```{r tbl-h3-num-dom, warning=FALSE, eval=FALSE}
#| tbl-cap: Results from all numerator models
models_tbl_h3_treatment_num_dom <- models_tbl_h3_treatment_num_dom %>% 
  set_names(1:length(.))

notes <- c(
  "Posterior medians; 95% credible intervals in brackets", 
  "Total \\(R^2\\) considers the variance of both population and group effects", 
  "Marginal \\(R^2\\) only takes population effects into account"
)

modelsummary(models_tbl_h3_treatment_num_dom,
             estimate = "{estimate}",
             statistic = "[{conf.low}, {conf.high}]",
             add_rows = treatment_rows,
             coef_map = coefs_num,
             gof_map = gofs,
             output = "kableExtra",
             fmt =  list(estimate = 2, conf.low = 2, conf.high = 2)) %>% 
  row_spec(1, bold = TRUE) %>% 
  kable_styling(htmltable_class = "table-sm light-border")
```

#### Denominator

```{r tbl-h3-denom-dom, warning=FALSE, eval=FALSE}
#| tbl-cap: Results from all numerator models
models_tbl_h3_treatment_denom_dom <- models_tbl_h3_treatment_denom_dom %>% 
  set_names(1:length(.))

notes <- c(
  "Posterior medians; 95% credible intervals in brackets", 
  "Total \\(R^2\\) considers the variance of both population and group effects", 
  "Marginal \\(R^2\\) only takes population effects into account"
)

modelsummary(models_tbl_h3_treatment_denom_dom,
             estimate = "{estimate}",
             statistic = "[{conf.low}, {conf.high}]",
             add_rows = treatment_rows,
             coef_map = coefs_denom,
             gof_map = gofs,
             fmt =  list(estimate = 2, conf.low = 2, conf.high = 2),
             notes = notes) %>% 
  row_spec(1, bold = TRUE) %>% 
  kable_styling(htmltable_class = "table-sm light-border")
```

:::

### % of aid to foreign NGO recipients

::: {.panel-tabset}

#### Numerator

```{r tbl-h3-num-foreign, warning=FALSE, eval=FALSE}
#| tbl-cap: Results from all numerator models
models_tbl_h3_treatment_num_foreign <- models_tbl_h3_treatment_num_foreign %>% 
  set_names(1:length(.))

notes <- c(
  "Posterior medians; 95% credible intervals in brackets", 
  "Total \\(R^2\\) considers the variance of both population and group effects", 
  "Marginal \\(R^2\\) only takes population effects into account"
)

modelsummary(models_tbl_h3_treatment_num_foreign,
             estimate = "{estimate}",
             statistic = "[{conf.low}, {conf.high}]",
             add_rows = treatment_rows,
             coef_map = coefs_num,
             gof_map = gofs,
             output = "kableExtra",
             fmt =  list(estimate = 2, conf.low = 2, conf.high = 2)) %>% 
  row_spec(1, bold = TRUE) %>% 
  kable_styling(htmltable_class = "table-sm light-border")
```

#### Denominator

```{r tbl-h3-denom-foreign, warning=FALSE, eval=FALSE}
#| tbl-cap: Results from all numerator models
models_tbl_h3_treatment_denom_foreign <- models_tbl_h3_treatment_denom_foreign %>% 
  set_names(1:length(.))

notes <- c(
  "Posterior medians; 95% credible intervals in brackets", 
  "Total \\(R^2\\) considers the variance of both population and group effects", 
  "Marginal \\(R^2\\) only takes population effects into account"
)

modelsummary(models_tbl_h3_treatment_denom_foreign,
             estimate = "{estimate}",
             statistic = "[{conf.low}, {conf.high}]",
             add_rows = treatment_rows,
             coef_map = coefs_denom,
             gof_map = gofs,
             fmt =  list(estimate = 2, conf.low = 2, conf.high = 2),
             notes = notes) %>% 
  row_spec(1, bold = TRUE) %>% 
  kable_styling(htmltable_class = "table-sm light-border")
```

:::

::::


# Outcome models

Our outcome variable for these hypotheses is the proportion of USAID aid allocated to (1) domestic and (2) foreign NGOs, which are (1) bounded between 0% and 100% and (2) have a lot of zeros.

```{r tbl-zero-summary}
#| tbl-cap: 0s in recipient outcomes
bind_rows(
  `Proportion of aid to domestic NGOs` = count(df_country_aid_laws, is_zero = prop_ngo_dom == 0),
  `Proportion of aid to foreign NGOs` = count(df_country_aid_laws, is_zero = prop_ngo_foreign == 0),
  .id = "Outcome"
) %>% 
  group_by(Outcome) %>% 
  mutate(`Number of 0s` = glue::glue("{n[2]} / {sum(n)}")) %>% 
  mutate(`Proportion of 0s` = label_percent(accuracy = 0.1)(n / sum(n))) %>% 
  ungroup() %>% 
  filter(is_zero) %>% select(-is_zero, -n) %>% 
  kbl(align = c("l", "c", "c")) %>% 
  kable_styling(htmltable_class = "table table-sm",
                full_width = FALSE)
```

```{r plot-zero-recip, fig.width=8, fig.height=3.5}
#| out-width: 90%
#| column: page-inset-right
p1 <- df_country_aid_laws %>%
  mutate(is_zero = prop_ngo_dom == 0) %>% 
  mutate(prop_ngo_dom = ifelse(is_zero, -0.05, prop_ngo_dom))  %>%  
  ggplot(aes(x = prop_ngo_dom)) +
  geom_histogram(aes(fill = is_zero), binwidth = 0.05, 
                 linewidth = 0.25, boundary = 0, color = "white") +
  geom_vline(xintercept = 0) + 
  scale_x_continuous(labels = label_percent()) +
  scale_y_continuous(labels = label_comma()) +
  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[8]), 
                    guide = guide_legend(reverse = TRUE)) +
  labs(x = "Proportion of aid to domestic NGOs", y = NULL, fill = "Is zero?") +
  coord_cartesian(ylim = c(0, 1500)) +
  theme_donors() +
  theme(legend.position = "bottom")

p2 <- df_country_aid_laws %>%
  mutate(is_zero = prop_ngo_foreign == 0) %>% 
  mutate(prop_ngo_foreign = ifelse(is_zero, -0.05, prop_ngo_foreign))  %>%  
  ggplot(aes(x = prop_ngo_foreign)) +
  geom_histogram(aes(fill = is_zero), binwidth = 0.05, 
                 linewidth = 0.25, boundary = 0, color = "white") +
  geom_vline(xintercept = 0) + 
  scale_x_continuous(labels = label_percent()) +
  scale_y_continuous(labels = label_comma()) +
  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[8]), 
                    guide = guide_legend(reverse = TRUE)) +
  labs(x = "Proportion of aid to foreign NGOs", y = NULL, fill = "Is zero?") +
  coord_cartesian(ylim = c(0, 1500)) +
  theme_donors() +
  theme(legend.position = "bottom")

(p1 | p2) +
  plot_layout(guides = "collect") +
  plot_annotation(theme = theme(legend.position = "bottom"))
```

Because of this distribution, we use a zero-inflated beta family to model the outcome. [This guide to working with tricky outcomes with lots of zeros](model-tricky-outcomes.qmd#zero-inflated-models-proportions) explores all the intricacies of zero-inflated beta families, so we won't go into tons of detail here.

As with total foreign aid and aid contentiousness, we’re not entirely sure what the actual underlying zero process is for the proportion of aid to different recipients. There's definitely a time-related aspect—aid to both kinds of NGOs decreases over time (replaced with corresponding increases to  governments and multilateral organizations like regional development banks). The trend is fairly linear, but to stay consistent with our hurdle and zero-inflated modeling strategies from the previous hypotheses, we still include year squared in the model.

```{r plot-prop-zero-zi, fig.width=8, fig.height=3.5}
#| out-width: 90%
#| column: page-inset-right
p1 <- df_country_aid_laws %>% 
  group_by(year) %>% 
  summarize(prop_zero = mean(prop_ngo_dom == 0)) %>% 
  ggplot(aes(x = year, y = prop_zero)) +
  geom_line(linewidth = 0.5, color = "grey70") +
  geom_point(size = 1) + 
  geom_smooth(aes(color = "y = x"), method = "lm", 
              formula = y ~ x, se = FALSE) +
  geom_smooth(aes(color = "y = x + x<sup>2</sup>"), method = "lm", 
              formula = y ~ x + I(x^2), se = FALSE) +
  scale_y_continuous(labels = label_percent()) +
  scale_color_manual(values = clrs$Prism[c(3, 11)]) +
  labs(x = NULL, y = "Proportion of countries\nwith zero aid to domestic NGOs",
       color = NULL) +
  coord_cartesian(ylim = c(0.15, 0.45)) +
  theme_donors() +
  theme(legend.text = element_markdown())

p2 <- df_country_aid_laws %>% 
  group_by(year) %>% 
  summarize(prop_zero = mean(prop_ngo_foreign == 0)) %>% 
  ggplot(aes(x = year, y = prop_zero)) +
  geom_line(linewidth = 0.5, color = "grey70") +
  geom_point(size = 1) + 
  geom_smooth(aes(color = "y = x"), method = "lm", 
              formula = y ~ x, se = FALSE) +
  geom_smooth(aes(color = "y = x + x<sup>2</sup>"), method = "lm", 
              formula = y ~ x + I(x^2), se = FALSE) +
  scale_y_continuous(labels = label_percent()) +
  scale_color_manual(values = clrs$Prism[c(3, 11)]) +
  labs(x = NULL, y = "Proportion of countries\nwith zero aid to foreign NGOs",
       color = NULL) +
  coord_cartesian(ylim = c(0.15, 0.45)) +
  theme_donors() +
  theme(legend.text = element_markdown())

(p1 | p2) +
  plot_layout(guides = "collect") +
  plot_annotation(theme = theme(legend.position = "bottom"))
```


## Formal model and priors

Our final models look like this (again with `treatment` replaced by the actual treatment column):

:::: {.panel-tabset}

#### Domestic NGO recipients

```{r fake-outcome-dom, eval=FALSE}
#| code-fold: show
bf(prop_ngo_dom | weights(iptw) ~ treatment_lag1 + treatment_lag2_cumsum +
     year_c + (1 + year_c | gwcode),
   zi ~ year_c + I(year_c^2))
```

#### Foreign NGO recipients

```{r fake-outcome-foreign, eval=FALSE}
#| code-fold: show
bf(prop_ngo_foreign | weights(iptw) ~ treatment_lag1 + treatment_lag2_cumsum +
     year_c + (1 + year_c | gwcode),
   zi ~ year_c + I(year_c^2))
```

:::

Or more formally:

::: {.column-page-inset-right}

$$
\begin{aligned}
&\ \mathrlap{\textbf{Zero-inflated model of proportion $i$ across time $t$ within each country $j$}} \\
\text{Proportion}_{it_j} \sim&\ \mathrlap{\begin{cases}
0 & \text{with probability } \pi_{it} + [(1 - \pi_{it}) \times \operatorname{Beta}(0 \mid \mu_{it_j}, \phi_y)] \\[4pt]
\operatorname{Beta}(\mu_{it_j}, \phi_y) & \text{with probability } (1 - \pi_{it}) \times \operatorname{Beta}(\text{Proportion}_{it_j} \mid \mu_{it_j}, \phi_y)
\end{cases}} \\
\\
&\ \textbf{Models for distribution parameters} \\
\operatorname{logit}(\pi_{it}) =&\ \gamma_0 + \gamma_1 \text{Year}_{it} + \gamma_2 \text{Year}^2_{it} & \text{Zero-inflation process} \\[4pt]
\operatorname{logit}(\mu_{it_j}) =&\ \text{IPTW}_{i, t-1_j} \times \Bigl[ (\beta_0 + b_{0_j}) + \beta_1\, \text{Treatment}_{i, t-1_j} + \\
&\ \beta_2\, \textstyle{\sum_{\tau = (t-2)}^{t}} \text{Treatment}_{i\tau} + (\beta_3 + b_{3_j}) \text{Year}_{it_j} \Bigr] & \text{Within-country variation} \\[4pt]
\left(
  \begin{array}{c} 
  b_{0_j} \\
  b_{3_j}
  \end{array}
\right) 
\sim&\ \text{MV}\,\mathcal{N}
\left[
  \left(
    \begin{array}{c}
    0 \\
    0 \\
    \end{array}
  \right)
  , \,
  \left(
  \begin{array}{cc}
     \sigma^2_{0} & \rho_{0, 3}\, \sigma_{0} \sigma_{3} \\ 
     \cdots & \sigma^2_{3}
  \end{array}
\right)
\right] & \text{Variability in average intercepts and slopes} \\
\\
&\ \textbf{Priors} \\
\gamma_0 \sim&\ \text{Student $t$}(\nu = 3, \mu = 0, \sigma = 1.5) & \text{Prior for intercept in zero-inflated model} \\
\gamma_1, \gamma_2 \sim&\ \text{Student $t$}(3, 0, 1.5) & \text{Prior for year effect in zero-inflated model} \\
\beta_0 \sim&\ \text{Student $t$}(3, 0, 1.5) & \text{Prior for global average proportion} \\
\beta_1, \beta_2, \beta_3 \sim&\ \text{Student $t$}(3, 0, 1.5) & \text{Prior for global effects} \\
\phi_y \sim&\ \operatorname{Exponential}(1) & \text{Prior for within-country dispersion} \\
\sigma_0, \sigma_3 \sim&\ \operatorname{Exponential}(1) & \text{Prior for within-country variability} \\
\rho \sim&\ \operatorname{LKJ}(2) & \text{Prior for between-country variability}
\end{aligned}
$$

:::


## MCMC diagnostics

To check that everything converged nicely, we check some diagnostics for the outcome models for the total barriers treatment for domestic NGO recipients. All the other models look basically the same as this—everything's fine.

::: {.panel-tabset}

### Trace plots

```{r plot-outcome-trace, warning=FALSE}
#| out-width: 80%
m_recip_outcome_total_dom$model %>% 
  gather_draws(`^b_.*|^sd_.*|^phi`, regex = TRUE) %>% 
  ggplot(aes(x = .iteration, y = .value, color = factor(.chain))) +
  geom_line(linewidth = 0.1) +
  scale_color_manual(values = clrs$Sunset[3:6]) +
  facet_wrap(vars(.variable), scales = "free_y") +
  theme_donors()
```

### Trank plots

```{r plot-outcome-trank, warning=FALSE}
#| out-width: 80%
m_recip_outcome_total_dom$model %>% 
  gather_draws(`^b_.*|^sd_.*|^phi`, regex = TRUE) %>% 
  group_by(.variable) %>% 
  mutate(draw_rank = rank(.value)) %>% 
  ggplot(aes(x = draw_rank, color = factor(.chain))) +
  stat_bin(geom = "step", binwidth = 1000, position = position_identity(), boundary = 0) +
  scale_color_manual(values = clrs$Sunset[3:6]) +
  facet_wrap(vars(.variable), scales = "free_y") +
  theme_donors() +
  theme(axis.text.y = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank())
```

### Posterior predictive check

```{r plot-outcome-ppcheck, message=FALSE}
#| out-width: 80%
withr::with_seed(1234, {
  pp_check(m_recip_outcome_total_dom$model, ndraws = 20) +
    labs(x = "Proportion of aid to domestic NGOs",
         title = "Outcome model") +
    theme_donors() +
    coord_cartesian(xlim = c(0, 1))
})
```

:::


## Analyzing the posterior

### Average treatment effects

Just like the other hypotheses, we look at *conditional effects* here, or the effect of these various kinds of civil society restrictions in a typical country (where the country-specific $b$ offsets are set to zero).

:::: {.panel-tabset}

#### Total barriers

::: {.panel-tabset}
##### % of aid to domestic NGO recipients

Additional barriers of any type lead to a tiny more aid to domestic NGOs, with an average increase of 0.18 percentage points (and the probability of being greater than zero is 0.97). This encompasses multiple countervailing trends though, since barriers to advocacy decrease the amount and other barriers increase it.

```{r plot-cfx-range-total-dom}
#| out-width: 80%
m_recip_outcome_total_dom$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_total_dom$model,
                                 year_c = 0,
                                 barriers_total = seq(0, 10, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = barriers_total, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_continuous(breaks = seq(0, 10, by = 2)) +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Total barriers", y = "Predicted proportion of\naid to domestic NGOs in the following year") +
  theme_donors()
```

```{r cfx-mfx-total-dom}
mfx_recip_cfx_multiple_dom$total %>% 
  select(barriers_total, dydx, conf.low, conf.high)
```

```{r cfx-mfx-total-p-direction-dom}
mfx_total_p_direction_dom <- mfx_recip_cfx_multiple_dom$total %>% 
  posteriordraws() %>% 
  filter(barriers_total == 1) %>% 
  summarize(pd = sum(draw < 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-total-dom}
#| out-width: 80%
mfx_recip_cfx_multiple_dom$total %>% 
  posteriordraws() %>% 
  filter(barriers_total %in% c(1, 7)) %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(barriers_total))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(2, 4, 6)]) +
  labs(x = "Conditional effect of total barriers on\nproportion of aid to domestic NGOs in the following year", y = NULL,
       subtitle = glue("P(ATE > 0) = {1 - pull(mfx_total_p_direction_dom, pd_short)}"), fill = NULL) +
  theme_donors()
```

##### % of aid to foreign NGO recipients

Additional legal barriers of any type slightly increase the proportion allocated to foreign NGOs by 0.34 percentage points, but the probability that that's greater than zero is only 0.72.

```{r plot-cfx-range-total-foreign}
#| out-width: 80%
m_recip_outcome_total_foreign$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_total_foreign$model,
                                 year_c = 0,
                                 barriers_total = seq(0, 10, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = barriers_total, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_continuous(breaks = seq(0, 10, by = 2)) +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Total barriers", y = "Predicted proportion of\naid to foreign NGOs in the following year") +
  theme_donors()
```

```{r cfx-mfx-total-foreign}
mfx_recip_cfx_multiple_foreign$total %>% 
  select(barriers_total, dydx, conf.low, conf.high)
```

```{r cfx-mfx-total-p-direction-foreign}
mfx_total_p_direction_foreign <- mfx_recip_cfx_multiple_foreign$total %>% 
  posteriordraws() %>% 
  filter(barriers_total == 1) %>% 
  summarize(pd = sum(draw < 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-total-foreign}
#| out-width: 80%
mfx_recip_cfx_multiple_foreign$total %>% 
  posteriordraws() %>% 
  filter(barriers_total %in% c(1, 7)) %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(barriers_total))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(2, 4, 6)]) +
  labs(x = "Conditional effect of total barriers on\nproportion of aid to foreign NGOs in the following year", y = NULL,
       subtitle = glue("P(ATE > 0) = {1 - pull(mfx_total_p_direction_foreign, pd_short)}"), fill = NULL) +
  theme_donors()
```
:::

#### Advocacy

::: {.panel-tabset}
##### % of aid to domestic NGO recipients

The story of advocacy laws is fascinating!. Additional barriers to advocacy decrease the amount of aid allocated to domestic NGOs, with a marginal effect of -0.6 percentage points (and a probability of being less than zero of 0.92). 

```{r plot-cfx-range-advocacy-dom}
#| out-width: 80%
m_recip_outcome_advocacy_dom$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_advocacy_dom$model,
                                 year_c = 0,
                                 advocacy = seq(0, 2, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = advocacy, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_continuous(breaks = 0:2) +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Barriers to advocacy", y = "Predicted proportion of\naid to domestic NGOs in the following year") +
  theme_donors()
```

```{r cfx-mfx-advocacy-dom}
mfx_recip_cfx_multiple_dom$advocacy %>% 
  select(advocacy, dydx, conf.low, conf.high)
```

```{r cfx-mfx-advocacy-p-direction-dom}
mfx_advocacy_p_direction_dom <- mfx_recip_cfx_multiple_dom$advocacy %>% 
  posteriordraws() %>% 
  filter(advocacy == 1) %>% 
  summarize(pd = sum(draw > 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-advocacy-dom}
#| out-width: 80%
mfx_recip_cfx_multiple_dom$advocacy %>% 
  posteriordraws() %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(advocacy))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(2, 4, 6)]) +
  labs(x = "Conditional effect of barriers to advocacy on\nproportion of aid to domestic NGOs in the following year", y = NULL,
       subtitle = glue("P(ATE < 0) = {1 - pull(mfx_advocacy_p_direction_dom, pd_short)}"), fill = NULL) +
  theme_donors()
```

##### % of aid to foreign NGO recipients

In contrast, however, additional barriers to advocacy increase the amount of aid allocated to foreign NGOs, with a marginal effect of 3 percentage points (and a probability of being greater than zero of 0.88)

```{r plot-cfx-range-advocacy-foreign}
#| out-width: 80%
m_recip_outcome_advocacy_foreign$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_advocacy_foreign$model,
                                 year_c = 0,
                                 advocacy = seq(0, 2, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = advocacy, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_continuous(breaks = 0:2) +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Barriers to advocacy", y = "Predicted proportion of\naid to foreign NGOs in the following year") +
  theme_donors()
```

```{r cfx-mfx-advocacy-foreign}
mfx_recip_cfx_multiple_foreign$advocacy %>% 
  select(advocacy, dydx, conf.low, conf.high)
```

```{r cfx-mfx-advocacy-p-direction-foreign}
mfx_advocacy_p_direction_foreign <- mfx_recip_cfx_multiple_foreign$advocacy %>% 
  posteriordraws() %>% 
  filter(advocacy == 1) %>% 
  summarize(pd = sum(draw > 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-advocacy-foreign}
#| out-width: 80%
mfx_recip_cfx_multiple_foreign$advocacy %>% 
  posteriordraws() %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(advocacy))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(2, 4, 6)]) +
  labs(x = "Conditional effect of barriers to advocacy on\nproportion of aid to foreign NGOs in the following year", y = NULL,
       subtitle = glue("P(ATE > 0) = {pull(mfx_advocacy_p_direction_foreign, pd_short)}"), fill = NULL) +
  theme_donors()
```

:::

#### Entry

::: {.panel-tabset}
##### % of aid to domestic NGO recipients

Additional barriers to entry increase the proportion of aid allocated to domestic NGOs, with a marginal effect of 0.4 percentage points (and a probability of being greater than zero of 0.97).

```{r plot-cfx-range-entry-dom}
#| out-width: 80%
m_recip_outcome_entry_dom$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_entry_dom$model,
                                 year_c = 0,
                                 entry = seq(0, 3, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = entry, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_continuous(breaks = 0:3) +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Barriers to entry", y = "Predicted proportion of\naid to domestic NGOs in the following year") +
  theme_donors()
```

```{r cfx-mfx-entry-dom}
mfx_recip_cfx_multiple_dom$entry %>% 
  select(entry, dydx, conf.low, conf.high)
```

```{r cfx-mfx-entry-p-direction-dom}
mfx_entry_p_direction_dom <- mfx_recip_cfx_multiple_dom$entry %>% 
  posteriordraws() %>% 
  filter(entry == 1) %>% 
  summarize(pd = sum(draw > 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-entry-dom}
#| out-width: 80%
mfx_recip_cfx_multiple_dom$entry %>% 
  posteriordraws() %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(entry))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(2, 4, 6, 7)]) +
  labs(x = "Conditional effect of barriers to entry on\nproportion of aid to domestic NGOs in the following year", y = NULL,
       subtitle = glue("P(ATE > 0) = {pull(mfx_entry_p_direction_dom, pd_short)}"), fill = NULL) +
  theme_donors()
```

##### % of aid to foreign NGO recipients

Barriers to entry kind of increase the amount of aid given to foreign NGOs too, but the signal is a little weaker and uncertain. The marginal effect is almost 1 percentage point (0.95), but the probability that that's greater than zero is 0.82.

```{r plot-cfx-range-entry-foreign}
#| out-width: 80%
m_recip_outcome_entry_foreign$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_entry_foreign$model,
                                 year_c = 0,
                                 entry = seq(0, 3, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = entry, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_continuous(breaks = 0:3) +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Barriers to entry", y = "Predicted proportion of\naid to foreign NGOs in the following year") +
  theme_donors()
```

```{r cfx-mfx-entry-foreign}
mfx_recip_cfx_multiple_foreign$entry %>% 
  select(entry, dydx, conf.low, conf.high)
```

```{r cfx-mfx-entry-p-direction-foreign}
mfx_entry_p_direction_foreign <- mfx_recip_cfx_multiple_foreign$entry %>% 
  posteriordraws() %>% 
  filter(entry == 1) %>% 
  summarize(pd = sum(draw > 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-entry-foreign}
#| out-width: 80%
mfx_recip_cfx_multiple_foreign$entry %>% 
  posteriordraws() %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(entry))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(2, 4, 6, 7)]) +
  labs(x = "Conditional effect of barriers to entry on\nproportion of aid to foreign NGOs in the following year", y = NULL,
       subtitle = glue("P(ATE > 0) = {pull(mfx_entry_p_direction_foreign, pd_short)}"), fill = NULL) +
  theme_donors()
```

:::

#### Funding

::: {.panel-tabset}
##### % of aid to domestic NGO recipients

Additional barriers to funding increase the proportion of aid given to domestic NGOs, with a marginal effect of half a percentage point (0.47), which is definitely greater than zero (0.98).

```{r plot-cfx-range-funding-dom}
#| out-width: 80%
m_recip_outcome_funding_dom$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_funding_dom$model,
                                 year_c = 0,
                                 funding = seq(0, 4, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = funding, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_continuous(breaks = 0:4) +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Barriers to funding", y = "Predicted proportion of\naid to domestic NGOs in the following year") +
  theme_donors()
```

```{r cfx-mfx-funding-dom}
mfx_recip_cfx_multiple_dom$funding %>% 
  select(funding, dydx, conf.low, conf.high)
```

```{r cfx-mfx-funding-p-direction-dom}
mfx_funding_p_direction_dom <- mfx_recip_cfx_multiple_dom$funding %>% 
  posteriordraws() %>% 
  filter(funding == 1) %>% 
  summarize(pd = sum(draw < 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-funding-dom}
#| out-width: 80%
mfx_recip_cfx_multiple_dom$funding %>% 
  posteriordraws() %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(funding))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(1, 2, 4, 6, 7)]) +
  labs(x = "Conditional effect of barriers to funding on\nproportion of aid to domestic NGOs in the following year", y = NULL,
       subtitle = glue("P(ATE > 0) = {1 - pull(mfx_funding_p_direction_dom, pd_short)}"), fill = NULL) +
  theme_donors()
```

##### % of aid to foreign NGO recipients

Additional barriers to funding also increase the amount of aid allocated to foreign NGOs, but the effect is far more uncertain here. The median is 0.43 percentage points, but the probability of being greater than zero is only 0.64—there's a good chance it could be negative or nothing at all.

```{r plot-cfx-range-funding-foreign}
#| out-width: 80%
m_recip_outcome_funding_foreign$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_funding_foreign$model,
                                 year_c = 0,
                                 funding = seq(0, 4, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = funding, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_continuous(breaks = 0:4) +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Barriers to funding", y = "Predicted proportion of\naid to foreign NGOs in the following year") +
  theme_donors()
```

```{r cfx-mfx-funding-foreign}
mfx_recip_cfx_multiple_foreign$funding %>% 
  select(funding, dydx, conf.low, conf.high)
```

```{r cfx-mfx-funding-p-direction-foreign}
mfx_funding_p_direction_foreign <- mfx_recip_cfx_multiple_foreign$funding %>% 
  posteriordraws() %>% 
  filter(funding == 1) %>% 
  summarize(pd = sum(draw < 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-funding-foreign}
#| out-width: 80%
mfx_recip_cfx_multiple_foreign$funding %>% 
  posteriordraws() %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(funding))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(1, 2, 4, 6, 7)]) +
  labs(x = "Conditional effect of barriers to funding on\nproportion of aid to foreign NGOs in the following year", y = NULL,
       subtitle = glue("P(ATE > 0) = {1 - pull(mfx_funding_p_direction_foreign, pd_short)}"), fill = NULL) +
  theme_donors()
```

:::

#### Core civil society index

::: {.panel-tabset}
##### % of aid to domestic NGO recipients

De facto civil society regulations tell a slightly different story. As the general legal environment gets worse, the proportion of aid allocated to dometic NGOs decreases, with a marginal effect of 0.15 percentage points (and a 100% probability of being positive). 

```{r plot-cfx-range-ccsi-dom}
#| out-width: 80%
m_recip_outcome_ccsi_dom$model_50 %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_ccsi_dom$model_50,
                                 year_c = 0,
                                 v2xcs_ccsi = seq(1, 0, -0.1)),
              re_formula = NA) %>% 
  ggplot(aes(x = v2xcs_ccsi, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_reverse() +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Core civil society index", y = "Predicted proportion of\naid to domestic NGOs in the following year",
       caption = "**x-axis reversed**; lower values represent worse respect for civil society") +
  theme_donors() +
  theme(plot.caption = element_markdown())
```

```{r cfx-mfx-ccsi-dom}
mfx_recip_cfx_multiple_dom$ccsi %>% 
  select(v2xcs_ccsi, dydx, conf.low, conf.high)
```

```{r cfx-mfx-ccsi-p-direction-dom}
mfx_ccsi_p_direction_dom <- mfx_recip_cfx_multiple_dom$ccsi %>% 
  posteriordraws() %>% 
  filter(v2xcs_ccsi == 0.5) %>% 
  summarize(pd = sum(draw < 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-ccsi-dom}
#| out-width: 80%
mfx_recip_cfx_multiple_dom$ccsi %>% 
  posteriordraws() %>% 
  mutate(draw = -draw) %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(v2xcs_ccsi))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(1, 2, 4, 6, 7)]) +
  labs(x = "Conditional effect of core civil society index on\nproportion of aid to domestic NGOs in the following year", y = NULL,
       subtitle = glue("P(ATE < 0) = {1 - pull(mfx_ccsi_p_direction_dom, pd_short)}"), fill = NULL) +
  theme_donors()
```

##### % of aid to foreign NGO recipients

In contrast, a worsening environment for civil society causes a substantial increase in the proportion of aid allocated to foreign NGOs, with a huge marginal effect of 2.7 percentage points (and 100% chance of being positive). USAID seems to rely heavily on foreign NGOs in countries with restrictive civil society.

```{r plot-cfx-range-ccsi-foreign}
#| out-width: 80%
m_recip_outcome_ccsi_foreign$model_50 %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_ccsi_foreign$model_50,
                                 year_c = 0,
                                 v2xcs_ccsi = seq(0, 1, 0.1)),
              re_formula = NA) %>% 
  ggplot(aes(x = v2xcs_ccsi, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_reverse() +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Core civil society index", y = "Predicted proportion of\naid to foreign NGOs in the following year",
       caption = "**x-axis reversed**; lower values represent worse respect for civil society") +
  theme_donors() +
  theme(plot.caption = element_markdown())
```

```{r cfx-mfx-ccsi-foreign}
mfx_recip_cfx_multiple_foreign$ccsi %>% 
  select(v2xcs_ccsi, dydx, conf.low, conf.high)
```

```{r cfx-mfx-ccsi-p-direction-foreign}
mfx_ccsi_p_direction_foreign <- mfx_recip_cfx_multiple_foreign$ccsi %>% 
  posteriordraws() %>% 
  filter(v2xcs_ccsi == 0.5) %>% 
  summarize(pd = sum(draw < 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-ccsi-foreign}
#| out-width: 80%
mfx_recip_cfx_multiple_foreign$ccsi %>% 
  posteriordraws() %>% 
  mutate(draw = -draw) %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(v2xcs_ccsi))) +
  stat_halfeye(alpha = 0.7) +
  scale_fill_manual(values = clrs$Sunset[c(1, 2, 4, 6, 7)]) +
  labs(x = "Conditional effect of core civil society index on\nproportion of aid to foreign NGOs in the following year", y = NULL,
       subtitle = glue("P(ATE > 0) = {pull(mfx_ccsi_p_direction_foreign, pd_short)}"), fill = NULL) +
  theme_donors()
```

:::

#### Civil society repression

::: {.panel-tabset}
##### % of aid to domestic NGO recipients

With civil society repression, there's again a slightly different story. Worsening repression leads to a little more aid allocated to domestic NGOs, with a marginal effect of 0.13 percentage points (and a 100% probability that that's positive).

```{r plot-cfx-range-repress-dom}
#| out-width: 80%
m_recip_outcome_repress_dom$model_50 %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_repress_dom$model_50,
                                 year_c = 0,
                                 v2csreprss = seq(-4, 3, 0.25)),
              re_formula = NA)  %>% 
  ggplot(aes(x = v2csreprss, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_reverse() +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Civil society repression", y = "Predicted proportion of\naid to domestic NGOs in the following year",
       caption = "**x-axis reversed**; lower values represent worse civil society repression") +
  theme_donors() +
  theme(plot.caption = element_markdown())
```

```{r cfx-mfx-repress-dom}
mfx_recip_cfx_multiple_dom$repress %>% 
  select(v2csreprss, dydx, conf.low, conf.high)
```

```{r cfx-mfx-repress-p-direction-dom}
mfx_repress_p_direction_dom <- mfx_recip_cfx_multiple_dom$repress %>% 
  posteriordraws() %>% 
  filter(v2csreprss == 0) %>% 
  summarize(pd = sum(draw < 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-repress-dom}
#| out-width: 80%
mfx_recip_cfx_multiple_dom$repress %>% 
  posteriordraws() %>% 
  mutate(draw = -draw) %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(v2csreprss))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(1, 2, 4, 6, 7)]) +
  labs(x = "Conditional effect of civil society repression on\nproportion of aid to domestic NGOs in the following year", y = NULL,
       subtitle = glue("P(ATE > 0) = {pull(mfx_repress_p_direction_dom, pd_short)}"), fill = NULL) +
  theme_donors()
```

##### % of aid to foreign NGO recipients

Even more striking, though, is USAID's response with foreign NGO recipients. As civil society repression increases, **WAY** more aid is sent through foreign NGOs, with a marginal effect of 5.5 percentage points(!) (and a 100% probability of being positive).

```{r plot-cfx-range-repress-foreign}
#| out-width: 80%
m_recip_outcome_repress_foreign$model_50 %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_repress_foreign$model_50,
                                 year_c = 0,
                                 v2csreprss = seq(-4, 3, 0.25)),
              re_formula = NA)  %>% 
  ggplot(aes(x = v2csreprss, y = .epred)) +
  stat_lineribbon(color = clrs$Peach[7]) +
  scale_x_reverse() +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(values = clrs$Peach[1:3]) +
  guides(fill = "none") +
  labs(x = "Civil society repression", y = "Predicted proportion of\naid to foreign NGOs in the following year",
       caption = "**x-axis reversed**; lower values represent worse civil society repression") +
  theme_donors() +
  theme(plot.caption = element_markdown())
```

```{r cfx-mfx-repress-foreign}
mfx_recip_cfx_multiple_foreign$repress %>% 
  select(v2csreprss, dydx, conf.low, conf.high)
```

```{r cfx-mfx-repress-p-direction-foreign}
mfx_repress_p_direction_foreign <- mfx_recip_cfx_multiple_foreign$repress %>% 
  posteriordraws() %>% 
  filter(v2csreprss == 0) %>% 
  summarize(pd = sum(draw < 0) / n()) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r plot-cfx-mfx-repress-foreign}
#| out-width: 80%
mfx_recip_cfx_multiple_foreign$repress %>% 
  posteriordraws() %>% 
  mutate(draw = -draw) %>% 
  pivot_longer(draw) %>% 
  ggplot(aes(x = value, fill = factor(v2csreprss))) +
  stat_halfeye(alpha = 0.7) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  scale_fill_manual(values = clrs$Sunset[c(1, 2, 4, 6, 7)]) +
  labs(x = "Conditional effect of civil society repression on\nproportion of aid to foreign NGOs in the following year", y = NULL,
       subtitle = glue("P(ATE > 0) = {pull(mfx_repress_p_direction_foreign, pd_short)}"), fill = NULL) +
  theme_donors()
```

:::

::::


### Combined plots

#### Predictions: Proportion of aid to domestic NGOs

```{r build-cfx-predictions-combined-dom}
ci_cols <- c("grey70", "grey45", "grey20")

p1 <- m_recip_outcome_total_dom$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_total_dom$model,
                                 year_c = 0,
                                 barriers_total = seq(0, 10, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = barriers_total, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_continuous(breaks = seq(0, 10, by = 2)) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$PurpOr[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$PurpOr[c(1, 3, 5)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0, 0.085)) +
  facet_wrap(vars("Total barriers")) +
  theme_donors() + 
  theme(legend.margin = margin(l = 7.5, r = 7.5))

p2 <- m_recip_outcome_advocacy_dom$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_advocacy_dom$model,
                                 year_c = 0,
                                 advocacy = seq(0, 2, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = advocacy, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_continuous(breaks = 0:2) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Teal[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Teal[c(1, 3, 5)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0, 0.085)) +
  facet_wrap(vars("Barriers to advocacy")) +
  theme_donors() + 
  theme(legend.margin = margin(l = 7.5, r = 7.5))

p3 <- m_recip_outcome_entry_dom$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_entry_dom$model,
                                 year_c = 0,
                                 entry = seq(0, 3, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = entry, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_continuous(breaks = 0:3) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Emrld[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Emrld[c(1, 3, 5)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0, 0.085)) +
  facet_wrap(vars("Barriers to entry")) +
  theme_donors() + 
  theme(legend.margin = margin(l = 7.5, r = 7.5))

p4 <- m_recip_outcome_funding_dom$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_funding_dom$model,
                                 year_c = 0,
                                 funding = seq(0, 4, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = funding, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_continuous(breaks = 0:4) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Peach[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Peach[c(1, 3, 5)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0, 0.085)) +
  facet_wrap(vars("Barriers to funding")) +
  theme_donors() + 
  theme(legend.margin = margin(l = 7.5, r = 7.5))
```

```{r plot-cfx-predictions-combined-dom, fig.width=7, fig.height=5}
#| out-width: 90%
#| fig-cap: "The effect of de jure anti-NGO legal barriers on the predicted 
#|   proportion of USAID aid allocated to domestic NGOs in a typical country"

# Put the shared y-axis label in a separate plot and add it to the combined plot
# https://stackoverflow.com/a/66778622/120898
p_lab <- ggplot() + 
  annotate(geom = "text", x = 1, y = 1, angle = 90, size = 3.3, fontface = "bold",
           label = "Predicted proportion of\naid to domestic NGOs in the following year") +
  coord_cartesian(clip = "off") +
  theme_void()

(p_lab | 
    ((p1 | p2) / (p3 | p4) + 
       plot_layout(guides = "collect") + 
       plot_annotation(theme = theme(legend.position = "bottom")))) + 
  plot_layout(widths = c(0.05, 1))
```

```{r plot-cfx-predictions-defacto-dom, fig.width=7, fig.height=3.6}
#| out-width: 90%
#| fig-cap: "The effect of the de facto civil society legal environment on the 
#|   predicted proportion of USAID aid channeled to domestic NGOs aid in a 
#|   typical country"
p1 <- m_recip_outcome_ccsi_dom$model_50 %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_ccsi_dom$model_50,
                                 year_c = 0,
                                 v2xcs_ccsi = seq(0, 1, 0.1)),
              re_formula = NA) %>% 
  ggplot(aes(x = v2xcs_ccsi, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_reverse(breaks = seq(0, 1, by = 0.25)) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Sunset[4],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Sunset[c(1, 2, 3)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0, 0.04)) +
  facet_wrap(vars("Worsening core civil society index")) +
  theme_donors() +
  theme(legend.margin = margin(l = 7.5, r = 7.5))

p2 <- m_recip_outcome_repress_dom$model_50 %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_repress_dom$model_50,
                                 year_c = 0,
                                 v2csreprss = seq(-4, 3, 0.25)),
              re_formula = NA) %>% 
  ggplot(aes(x = v2csreprss, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_reverse(labels = label_number(style_negative = "minus")) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Sunset[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Sunset[c(4, 5, 6)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):",
       caption = "**x-axis reversed**; lower values represent worse respect for and repression of civil society") +
  coord_cartesian(ylim = c(0, 0.04)) +
  facet_wrap(vars("Worsening civil society repression")) +
  theme_donors() +
  theme(legend.margin = margin(l = 7.5, r = 7.5),
        plot.caption = element_markdown())

p_lab <- ggplot() + 
  annotate(geom = "text", x = 1, y = 1, angle = 90, size = 3.3, fontface = "bold",
           label = "Predicted proportion of\naid to domestic NGOs in the following year") +
  coord_cartesian(clip = "off") +
  theme_void()

(p_lab | 
    ((p1 | p2) + 
       plot_layout(guides = "collect") + 
       plot_annotation(theme = theme(legend.position = "bottom")))) + 
  plot_layout(widths = c(0.05, 1))
```

#### Conditional marginal effects: Proportion of aid to domestic NGOs

```{r calc-cfx-mfx-all-dom}
mfx_total_stats_dom <- mfx_recip_cfx_single_dom$total %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_advocacy_stats_dom <- mfx_recip_cfx_single_dom$advocacy %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_entry_stats_dom <- mfx_recip_cfx_single_dom$entry %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_funding_stats_dom <- mfx_recip_cfx_single_dom$funding %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_ccsi_stats_dom <- mfx_recip_cfx_single_dom$ccsi %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_repress_stats_dom <- mfx_recip_cfx_single_dom$repress %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r build-cfx-mfx-combined-dom}
p1 <- mfx_recip_cfx_single_dom$total %>% 
  posteriordraws() %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$PurpOr[6], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE > 0) = {1 - pull(mfx_total_stats_dom, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$PurpOr[4], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("One additional barrier of any type")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p2 <- mfx_recip_cfx_single_dom$advocacy %>% 
  posteriordraws() %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$Teal[4], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE < 0) = {pull(mfx_advocacy_stats_dom, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Teal[6], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("One additional barrier to advocacy")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p3 <- mfx_recip_cfx_single_dom$entry %>% 
  posteriordraws() %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$Emrld[4], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE > 0) = {1 - pull(mfx_entry_stats_dom, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Emrld[6], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("One additional barrier to entry")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p4 <- mfx_recip_cfx_single_dom$funding %>% 
  posteriordraws() %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$Peach[6], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE > 0) = {1 - pull(mfx_funding_stats_dom, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Peach[4], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("One additional barrier to funding")) +
  theme_donors() +
  theme(axis.text.y = element_blank())
```

```{r plot-cfx-mfx-combined-dom, fig.width=7, fig.height=5.5}
#| out-width: 90%
#| fig-cap: "The effect of one additional de jure anti-NGO legal barrier on the 
#|   proportion of USAID aid allocated to domestic NGOs in a typical country"
p_lab <- ggplot() + 
  annotate(geom = "text", x = 1, y = 1, size = 3.3, fontface = "bold",
           label = "Conditional effect of treatment on proportion\nof aid to domestic NGOs in the following year") +
  coord_cartesian(clip = "off") +
  theme_void()

(((p1 | p2) / (p3 | p4)) / p_lab) + 
  plot_layout(heights = c(1, 1, 0.2)) +
  plot_annotation(caption = "Point shows median value;\nthick bar = 80% credible interval; thin bar = 95% credible interval")
```

```{r plot-cfx-mfx-defacto-dom, fig.width=7, fig.height=3.6}
#| out-width: 90%
#| fig-cap: "The effect of changes in the de facto civil society legal 
#|   environment on the predicted proportion of USAID aid allocated to domestic 
#|   NGOs in a typical country"
p1 <- mfx_recip_cfx_single_dom$ccsi %>% 
  posteriordraws() %>% 
  mutate(draw = -draw / 10) %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$Sunset[4], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE < 0) = {1 - pull(mfx_ccsi_stats_dom, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Sunset[3], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("A 0.1 unit decrease (worsening) in\nthe core civil society index")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p2 <- mfx_recip_cfx_single_dom$repress %>% 
  posteriordraws() %>% 
  mutate(draw = -draw) %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x > 0)),
               fill = clrs$Sunset[6], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE > 0) = {pull(mfx_repress_stats_dom, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Sunset[3], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("A 1 unit increase (improvement) in\nthe civil society repression score")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p_lab <- ggplot() + 
  annotate(geom = "text", x = 1, y = 1, size = 3.3, fontface = "bold",
           label = "Conditional effect of treatment on proportion\nof aid to domestic NGOs in the following year") +
  coord_cartesian(clip = "off") +
  theme_void()

((p1 | p2) / p_lab) + 
  plot_layout(heights = c(1, 0.18)) +
  plot_annotation(caption = "Point shows median value;\nthick bar = 80% credible interval; thin bar = 95% credible interval")
```

#### Predictions: Proportion of aid to foreign NGOs

```{r build-cfx-predictions-combined-foreign}
ci_cols <- c("grey70", "grey45", "grey20")

p1 <- m_recip_outcome_total_foreign$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_total_foreign$model,
                                 year_c = 0,
                                 barriers_total = seq(0, 10, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = barriers_total, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_continuous(breaks = seq(0, 10, by = 2)) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$PurpOr[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$PurpOr[c(1, 3, 5)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0.15, 0.42)) +
  facet_wrap(vars("Total barriers")) +
  theme_donors() + 
  theme(legend.margin = margin(l = 7.5, r = 7.5))

p2 <- m_recip_outcome_advocacy_foreign$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_advocacy_foreign$model,
                                 year_c = 0,
                                 advocacy = seq(0, 2, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = advocacy, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_continuous(breaks = 0:2) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Teal[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Teal[c(1, 3, 5)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0.15, 0.42)) +
  facet_wrap(vars("Barriers to advocacy")) +
  theme_donors() + 
  theme(legend.margin = margin(l = 7.5, r = 7.5))

p3 <- m_recip_outcome_entry_foreign$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_entry_foreign$model,
                                 year_c = 0,
                                 entry = seq(0, 3, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = entry, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_continuous(breaks = 0:3) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Emrld[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Emrld[c(1, 3, 5)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0.15, 0.42)) +
  facet_wrap(vars("Barriers to entry")) +
  theme_donors() + 
  theme(legend.margin = margin(l = 7.5, r = 7.5))

p4 <- m_recip_outcome_funding_foreign$model %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_funding_foreign$model,
                                 year_c = 0,
                                 funding = seq(0, 4, 1)),
              re_formula = NA) %>% 
  ggplot(aes(x = funding, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_continuous(breaks = 0:4) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Peach[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Peach[c(1, 3, 5)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0.15, 0.42)) +
  facet_wrap(vars("Barriers to funding")) +
  theme_donors() + 
  theme(legend.margin = margin(l = 7.5, r = 7.5))
```

```{r plot-cfx-predictions-combined-foreign, fig.width=7, fig.height=5}
#| out-width: 90%
#| fig-cap: "The effect of de jure anti-NGO legal barriers on the predicted 
#|   proportion of USAID aid allocated to foreign NGOs in a typical country"

# Put the shared y-axis label in a separate plot and add it to the combined plot
# https://stackoverflow.com/a/66778622/120898
p_lab <- ggplot() + 
  annotate(geom = "text", x = 1, y = 1, angle = 90, size = 3.3, fontface = "bold",
           label = "Predicted proportion of\naid to foreign NGOs in the following year") +
  coord_cartesian(clip = "off") +
  theme_void()

(p_lab | 
    ((p1 | p2) / (p3 | p4) + 
       plot_layout(guides = "collect") + 
       plot_annotation(theme = theme(legend.position = "bottom")))) + 
  plot_layout(widths = c(0.05, 1))
```

```{r plot-cfx-predictions-defacto-foreign, fig.width=7, fig.height=3.6}
#| out-width: 90%
#| fig-cap: "The effect of the de facto civil society legal environment on the 
#|   predicted proportion of USAID aid channeled to foreign NGOs aid in a 
#|   typical country"
p1 <- m_recip_outcome_ccsi_foreign$model_50 %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_ccsi_foreign$model_50,
                                 year_c = 0,
                                 v2xcs_ccsi = seq(0, 1, 0.1)),
              re_formula = NA) %>% 
  ggplot(aes(x = v2xcs_ccsi, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_reverse(breaks = seq(0, 1, by = 0.25)) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Sunset[4],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Sunset[c(1, 2, 3)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):") +
  coord_cartesian(ylim = c(0, 0.6)) +
  facet_wrap(vars("Worsening core civil society index")) +
  theme_donors() +
  theme(legend.margin = margin(l = 7.5, r = 7.5))

p2 <- m_recip_outcome_repress_foreign$model_50 %>% 
  epred_draws(newdata = datagrid(model = m_recip_outcome_repress_foreign$model_50,
                                 year_c = 0,
                                 v2csreprss = seq(-4, 3, 0.25)),
              re_formula = NA) %>% 
  ggplot(aes(x = v2csreprss, y = .epred)) +
  stat_lineribbon(aes(color = "Posterior median"), 
                  alpha = 0.6, point_interval = median_hdci) +
  scale_x_reverse(labels = label_number(style_negative = "minus")) +
  scale_y_continuous(labels = label_percent(accuracy = 1)) +
  scale_color_manual(
    values = clrs$Sunset[7],
    guide = guide_legend(order = 1, 
                         override.aes = list(fill = NA, alpha = 1, color = "black"))
  ) +
  scale_fill_manual(
    values = clrs$Sunset[c(4, 5, 6)], 
    labels = function(x) label_percent()(as.numeric(x)),
    guide = guide_legend(order = 2, 
                         override.aes = list(color = NA, fill = ci_cols))
  ) +
  labs(x = NULL, y = NULL, color = NULL, fill = "Credible interval (HPDI):",
       caption = "**x-axis reversed**; lower values represent worse respect for and repression of civil society") +
  coord_cartesian(ylim = c(0, 0.6)) +
  facet_wrap(vars("Worsening civil society repression")) +
  theme_donors() +
  theme(legend.margin = margin(l = 7.5, r = 7.5),
        plot.caption = element_markdown())

p_lab <- ggplot() + 
  annotate(geom = "text", x = 1, y = 1, angle = 90, size = 3.3, fontface = "bold",
           label = "Predicted proportion of\naid to foreign NGOs in the following year") +
  coord_cartesian(clip = "off") +
  theme_void()

(p_lab | 
    ((p1 | p2) + 
       plot_layout(guides = "collect") + 
       plot_annotation(theme = theme(legend.position = "bottom")))) + 
  plot_layout(widths = c(0.05, 1))
```


#### Conditional marginal effects: Proportion of aid to foreign NGOs

```{r calc-cfx-mfx-all-foreign}
mfx_total_stats_foreign <- mfx_recip_cfx_single_foreign$total %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_advocacy_stats_foreign <- mfx_recip_cfx_single_foreign$advocacy %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_entry_stats_foreign <- mfx_recip_cfx_single_foreign$entry %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_funding_stats_foreign <- mfx_recip_cfx_single_foreign$funding %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_ccsi_stats_foreign <- mfx_recip_cfx_single_foreign$ccsi %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))

mfx_repress_stats_foreign <- mfx_recip_cfx_single_foreign$repress %>% 
  posteriordraws() %>% 
  summarize(pd = sum(draw < 0) / n(),
            mad = mad(draw),
            med_hdci = median_hdci(draw)) %>% 
  unnest(med_hdci) %>% 
  mutate(pd_short = round(pd, 2))
```

```{r build-cfx-mfx-combined-foreign}
p1 <- mfx_recip_cfx_single_foreign$total %>% 
  posteriordraws() %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$PurpOr[6], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE > 0) = {1 - pull(mfx_total_stats_foreign, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$PurpOr[4], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("One additional barrier of any type")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p2 <- mfx_recip_cfx_single_foreign$advocacy %>% 
  posteriordraws() %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$Teal[4], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE > 0) = {1 - pull(mfx_advocacy_stats_foreign, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Teal[6], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("One additional barrier to advocacy")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p3 <- mfx_recip_cfx_single_foreign$entry %>% 
  posteriordraws() %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$Emrld[4], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE > 0) = {1 - pull(mfx_entry_stats_foreign, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Emrld[6], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("One additional barrier to entry")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p4 <- mfx_recip_cfx_single_foreign$funding %>% 
  posteriordraws() %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$Peach[6], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE > 0) = {1 - pull(mfx_funding_stats_foreign, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Peach[4], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("One additional barrier to funding")) +
  theme_donors() +
  theme(axis.text.y = element_blank())
```

```{r plot-cfx-mfx-combined-foreign, fig.width=7, fig.height=5.5}
#| out-width: 90%
#| fig-cap: "The effect of one additional de jure anti-NGO legal barrier on the 
#|   proportion of USAID aid allocated to foreign NGOs in a typical country"
p_lab <- ggplot() + 
  annotate(geom = "text", x = 1, y = 1, size = 3.3, fontface = "bold",
           label = "Conditional effect of treatment on proportion\nof aid to domestic NGOs in the following year") +
  coord_cartesian(clip = "off") +
  theme_void()

(((p1 | p2) / (p3 | p4)) / p_lab) + 
  plot_layout(heights = c(1, 1, 0.2)) +
  plot_annotation(caption = "Point shows median value;\nthick bar = 80% credible interval; thin bar = 95% credible interval")
```

```{r plot-cfx-mfx-defacto-foreign, fig.width=7, fig.height=3.6}
#| out-width: 90%
#| fig-cap: "The effect of changes in the de facto civil society legal 
#|   environment on the predicted proportion of USAID aid allocated to foreign 
#|   NGOs in a typical country"
p1 <- mfx_recip_cfx_single_foreign$ccsi %>% 
  posteriordraws() %>% 
  mutate(draw = -draw / 10) %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x < 0)),
               fill = clrs$Sunset[4], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE > 0) = {pull(mfx_ccsi_stats_foreign, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Sunset[3], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("A 0.1 unit decrease (worsening) in\nthe core civil society index")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p2 <- mfx_recip_cfx_single_foreign$repress %>% 
  posteriordraws() %>% 
  mutate(draw = -draw) %>% 
  ggplot(aes(x = draw)) +
  stat_halfeye(aes(fill_ramp = after_stat(x > 0)),
               fill = clrs$Sunset[6], .width = c(0.8, 0.95),
               point_interval = median_hdci) +
  geom_vline(xintercept = 0, linewidth = 0.25) +
  annotate(geom = "richtext", label = glue("P(ATE > 0) = {pull(mfx_repress_stats_foreign, pd_short)}"),
           x = Inf, y = Inf, hjust = 1, vjust = 1, size = 3,
           label.color = NA, label.margin = unit(rep(0.5, 4), "lines")) +
  scale_x_continuous(labels = label_number(scale = 100, suffix = " pp.",
                                           style_negative = "minus")) +
  scale_fill_ramp_discrete(from = clrs$Sunset[3], guide = "none") +
  labs(x = NULL, y = NULL, fill = NULL) +
  facet_wrap(vars("A 1 unit decrease (worsening) in\nthe civil society repression score")) +
  theme_donors() +
  theme(axis.text.y = element_blank())

p_lab <- ggplot() + 
  annotate(geom = "text", x = 1, y = 1, size = 3.3, fontface = "bold",
           label = "Conditional effect of treatment on proportion\nof aid to domestic NGOs in the following year") +
  coord_cartesian(clip = "off") +
  theme_void()

((p1 | p2) / p_lab) + 
  plot_layout(heights = c(1, 0.15)) +
  plot_annotation(caption = "Point shows median value;\nthick bar = 80% credible interval; thin bar = 95% credible interval")
```


#### Table

With H~1~ we had to convert the dollar-scale treatment effects into percent changes to make them more interpretable, since we were working with millions of dollars. With this outcome, though, we're just working with a 0–100% range, so we can stick with percentage point-scale effects. 

```{r build-cfx-mfx-results-table}
signif_pp <- label_number(accuracy = 0.01, scale = 100, suffix = " pp.",
                          style_negative = "minus")
signif_no_pp <- label_number(accuracy = 0.01, scale = 100,
                             style_negative = "minus")

mfx_lookup <- tribble(
  ~term, ~Treatment,
  "barriers_total", "One additional barrier of any type",
  "advocacy", "One additional barrier to advocacy",
  "entry", "One additional barrier to entry",
  "funding", "One additional barrier to funding",
  "v2xcs_ccsi", "A 0.1 unit decrease in the core civil society index (i.e. worse environment)",
  "v2csreprss", "A 1 unit decrease in the civil society repression score (i.e. more repression)"
) %>% 
  mutate(Treatment = fct_inorder(Treatment))

mfx_all_posteriors_dom <- bind_rows(
  posteriordraws(mfx_recip_cfx_single_dom$total), 
  posteriordraws(mfx_recip_cfx_single_dom$advocacy), 
  posteriordraws(mfx_recip_cfx_single_dom$entry), 
  posteriordraws(mfx_recip_cfx_single_dom$funding),
  (posteriordraws(mfx_recip_cfx_single_dom$ccsi) %>% mutate(draw = draw / 10)),
  posteriordraws(mfx_recip_cfx_single_dom$repress)) %>% 
  mutate(id = "domestic")

mfx_all_posteriors_foreign <- bind_rows(
  posteriordraws(mfx_recip_cfx_single_foreign$total), 
  posteriordraws(mfx_recip_cfx_single_foreign$advocacy), 
  posteriordraws(mfx_recip_cfx_single_foreign$entry), 
  posteriordraws(mfx_recip_cfx_single_foreign$funding),
  (posteriordraws(mfx_recip_cfx_single_foreign$ccsi) %>% mutate(draw = draw / 10)),
  posteriordraws(mfx_recip_cfx_single_foreign$repress)) %>% 
  mutate(id = "foreign")

mfx_all_posteriors <- bind_rows(mfx_all_posteriors_dom,
                                mfx_all_posteriors_foreign) %>% 
  mutate(draw = ifelse(term %in% c("v2xcs_ccsi", "v2csreprss"), -draw, draw),
         dydx = ifelse(term %in% c("v2xcs_ccsi", "v2csreprss"), -dydx, dydx),
         conf.low_real = ifelse(term %in% c("v2xcs_ccsi", "v2csreprss"), -conf.high, conf.low),
         conf.high_real = ifelse(term %in% c("v2xcs_ccsi", "v2csreprss"), -conf.low, conf.high),
         conf.low = conf.low_real, conf.high = conf.high_real)

mfx_p_direction <- mfx_all_posteriors %>% 
  group_by(id, term) %>% 
  summarize(pd_lt = round(sum(draw < 0) / n(), 2),
            pd_gt = round(sum(draw > 0) / n(), 2))

mfx_medians <- mfx_all_posteriors %>% 
  group_by(id, term) %>% 
  median_hdci(draw) %>%
  left_join(mfx_p_direction, by = c("id", "term")) %>% 
  mutate(direction = case_when(
    draw > 0 & id == "domestic" ~ "more USAID aid through domestic NGOs in the next year",
    draw > 0 & id == "foreign" ~ "more USAID aid through foreign NGOs in the next year",
    draw < 0 & id == "domestic" ~ "less USAID aid through domestic NGOs in the next year",
    draw < 0 & id == "foreign" ~ "less USAID aid through foreign NGOs in the next year"
  )) %>% 
  mutate(pd = case_when(
    draw > 0 ~ pd_gt,
    draw < 0 ~ pd_lt
  )) %>% 
  mutate(pd_nice = label_percent(accuracy = 1)(pd)) %>% 
  mutate(across(c(draw, .upper), ~signif_pp(.))) %>% 
  mutate(.lower = signif_no_pp(.lower)) %>% 
  mutate(interval = glue("[{.lower}, {.upper}]")) %>% 
  mutate(draw_nice = glue("{draw}\n{interval}")) %>% 
  left_join(mfx_lookup, by = "term")

mfx_medians_with_plots <- mfx_medians %>% 
  group_by(id, term) %>% 
  nest() %>% 
  mutate(sparkplot = map(data, ~spark_bar(.x))) %>% 
  mutate(sparkname = glue("sparkplots/recipient_bar_{id}_{term}")) %>% 
  mutate(saved_plot = map2(sparkplot, sparkname, ~save_sparks(.x, .y)))

mfx_median_clean <- mfx_medians_with_plots %>% 
  ungroup() %>% 
  select(-sparkplot) %>% 
  unnest_wider(saved_plot) %>% 
  unnest(data) %>% 
  arrange(Treatment) %>% 
  mutate(Probability = "")
```

```{r cfx-mfx-results-table}
#| column: screen-inset-right
tbl_notes <- c("The probability denotes the percentage of the posterior distribution that falls above or below 0.",
               "Reported values are the median posterior marginal effect of each treatment variable on the outcome, multiplied by 100 to show percentage point changes; 95% highest posterior density intervals (HPDI) shown in brackets.")

mfx_median_clean_dom <- mfx_median_clean %>% 
  filter(id == "domestic") %>% 
  select(Treatment, direction, Probability, draw_nice, png)

mfx_median_clean_foreign <- mfx_median_clean %>% 
  filter(id == "foreign") %>% 
  select(Treatment, `direction ` = direction, 
         `Probability ` = Probability, `draw_nice ` = draw_nice, png)

select(mfx_median_clean_dom, -png) %>%
  left_join(select(mfx_median_clean_foreign, -png), by = "Treatment") %>% 
  mutate(across(c(draw_nice, `draw_nice `), ~str_replace(., "\\n", "<br>"))) %>% 
  set_names(c("Countries that add…",
              "…receive…", 
              paste0("Probability", footnote_marker_symbol(1)),
              paste0("Median", footnote_marker_symbol(2)),
              "…receive… ", 
              paste0("Probability ", footnote_marker_symbol(1)),
              paste0("Median ", footnote_marker_symbol(2)))) %>% 
  kbl(align = c("l", "l", "c", "c", "l", "c", "c"), escape = FALSE) %>% 
  kable_styling(htmltable_class = "table table-sm table-borderless") %>% 
  add_header_above(c(" " = 1, "% of USAID aid to domestic NGOs" = 3, "% of USAID aid to foreign NGOs" = 3)) %>% 
  pack_rows("De jure legislation", 1, 4, indent = FALSE) %>% 
  pack_rows("De facto enforcement", 5, 6, indent = FALSE) %>% 
  column_spec(1, width = "16%") %>% 
  column_spec(2, width = "15%") %>% 
  column_spec(3, image = mfx_median_clean_dom$png, width = "14%") %>% 
  column_spec(4, width = "13%") %>% 
  column_spec(5, width = "15%") %>% 
  column_spec(6, image = mfx_median_clean_foreign$png, width = "14%") %>% 
  column_spec(7, width = "13%") %>% 
  footnote(symbol = tbl_notes, footnote_as_chunk = FALSE)
```


### Within- and between-country variability (φ and σs)

```{r extract-sigmas-total, include=FALSE, warning=FALSE}
zi_coefs <- m_recip_outcome_total_dom$model %>% 
  tidy(effects = "fixed") %>% 
  mutate(term = janitor::make_clean_names(term)) %>% 
  mutate(across(c(estimate, conf.low, conf.high), list(exp = ~exp(.)))) %>% 
  split(~term)

sigmas_zi <- m_recip_outcome_total_dom$model %>% 
  tidy(parameters = c("sd_*", "phi")) %>% 
  select(-component) %>% 
  mutate(term = janitor::make_clean_names(term)) %>% 
  split(~term)

zimuint <- plogis(zi_coefs$intercept$estimate)
ziphi <- exp(sigmas_zi$phi$estimate)
```

The $\phi$ and $\sigma$ terms are roughly the same across all these different models, so we'll just show the results from the total barriers + domestic NGOs model here. We have three uncertainty-related terms to work with:

- $\phi_y$ (`phi`): the precision or variance of aid to domestic NGOs within countries. On the log scale, it's `r round(sigmas_zi$phi$estimate, 2)`, which is `r label_comma()(exp(sigmas_zi$phi$estimate))` when unlogged or exponentiated, which is incredibly precise. That gives us a posterior distribution of the non-zero-inflated part of the model of $\operatorname{Beta}(`r zimuint`, `r round(ziphi, 0)`)$ which looks like this, very narrowly focused around the baseline average 2001 proportion:

```{r plot-zi-phi, warning=FALSE, indent="  "}
#| out-width: 70%
beta_params <- m_recip_outcome_total_dom$model %>% 
  tidy(parameters = c("b_(Intercept)", "phi"))

beta_mu <- beta_params %>% 
  filter(term == "b_(Intercept)") %>% 
  pull(estimate)

beta_phi <- beta_params %>% 
  filter(term == "phi") %>% 
  pull(estimate)

ggplot() +
  stat_function(geom = "area", fill = clrs$Prism[7],
                fun = ~dprop(., mean = plogis(beta_mu), size = exp(beta_phi))) +
  scale_x_continuous(labels = label_percent(), limits = c(0.0425, 0.0437)) +
  labs(title = "Distribution of non-zero-inflated aid to domestic NGOs in 2001",
       subtitle = glue::glue("Beta(µ = plogis({round(beta_mu, 2)}), φ = exp({round(beta_phi, 2)})) or Beta(µ = {round(plogis(beta_mu), 3)}, φ = {round(exp(beta_phi), 0)})")) +
  theme_donors()
```

- $\sigma_0$ (`sd__(Intercept)` for the `gwcode` group): the variability between countries' baseline averages, or the variability around the $b_{0_j}$ offsets. Here it's `r round(sigmas_zi$sd_gwcode_intercept$estimate, 2)`, which means that across or between countries, the proportion of aid to domestic NGOs varies by 1.5ish logit units.

- $\sigma_3$ (`sd__year_c` for the `gwcode` group): the variability between countries' year effects, or the variability around the $b_{3_j}$ offsets. Here it's `r round(sigmas_zi$sd_gwcode_year_c$estimate, 2)`, which means that average year effects vary by 0.15ish logit units across or between countries.

```{r show-sigmas-zi, warning=FALSE}
#| code-fold: show
m_recip_outcome_total_dom$model %>% 
  tidy(parameters = c("sd_*", "phi")) %>% 
  select(-component)
```

### Full results table

Again, this is less important since we don't care about individual coefficients and instead care about conditional effects, but for the sake of full transparency (and to placate future reviewers), here's a table of all the results:

::: {.panel-tabset}
#### % of aid to domestic NGO recipients

```{r tbl-h3-outcome-dom, warning=FALSE}
#| tbl-cap: Results from all outcome models
models_tbl_h3_outcome_dejure_dom <- models_tbl_h3_outcome_dejure_dom %>% 
  set_names(1:length(.))

notes <- c(
  "Posterior medians; 95% credible intervals (HDPI) in brackets.", 
  "Total \\(R^2\\) considers the variance of both population and group effects;", 
  "marginal \\(R^2\\) only takes population effects into account"
)

modelsummary(models_tbl_h3_outcome_dejure_dom,
             estimate = "{estimate}",
             statistic = "[{conf.low}, {conf.high}]",
             add_rows = outcome_rows,
             coef_map = coefs_outcome,
             gof_map = gofs,
             output = "kableExtra",
             fmt =  list(estimate = 2, conf.low = 2, conf.high = 2)) %>% 
  row_spec(1, bold = TRUE) %>% 
  kable_styling(htmltable_class = "table-sm light-border") %>% 
  footnote(general = notes, footnote_as_chunk = TRUE)
```

#### % of aid to foreign NGO recipients

```{r tbl-h3-outcome-foreign, warning=FALSE}
#| tbl-cap: Results from all outcome models
models_tbl_h3_outcome_dejure_foreign <- models_tbl_h3_outcome_dejure_foreign %>% 
  set_names(1:length(.))

notes <- c(
  "Posterior medians; 95% credible intervals (HDPI) in brackets.", 
  "Total \\(R^2\\) considers the variance of both population and group effects;", 
  "marginal \\(R^2\\) only takes population effects into account"
)

modelsummary(models_tbl_h3_outcome_dejure_foreign,
             estimate = "{estimate}",
             statistic = "[{conf.low}, {conf.high}]",
             add_rows = outcome_rows,
             coef_map = coefs_outcome,
             gof_map = gofs,
             output = "kableExtra",
             fmt =  list(estimate = 2, conf.low = 2, conf.high = 2)) %>% 
  row_spec(1, bold = TRUE) %>% 
  kable_styling(htmltable_class = "table-sm light-border") %>% 
  footnote(general = notes, footnote_as_chunk = TRUE)
```

:::
