---
title: "Why hierarchical models?"
---

```{r setup, include=FALSE}
# tikz stuff
# Necessary for using dvisvgm on macOS
# See https://www.andrewheiss.com/blog/2021/08/27/tikz-knitr-html-svg-fun/
Sys.setenv(LIBGS = "/usr/local/share/ghostscript/9.53.3/lib/libgs.dylib.9.53")
```

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(scales)
library(patchwork)

tar_config_set(store = here::here('_targets'),
               script = here::here('_targets.R'))

font_opts <- list(extra.preamble = c("\\usepackage{libertine}", 
                                     "\\usepackage{libertinust1math}"),
                  dvisvgm.opts = "--font-format=woff")

# Load data 
# Plotting functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(misc_funs), .GlobalEnv))

df_country_aid <- tar_read(country_aid_final)
df_country_aid_laws <- filter(df_country_aid, laws)
```


# Hierarchical structure

```{r data-summary, include=FALSE}
details <- df_country_aid_laws %>% 
  distinct(year) %>% 
  summarize(num_years = n(),
            year_first = min(year),
            year_last = max(year)) %>% 
  bind_cols(tibble(num_countries = df_country_aid_laws %>% 
                     distinct(gwcode) %>% nrow())) %>% 
  as.list()
```

Our data includes information about `r details$num_countries` countries across `r details$num_years` years (from `r details$year_first`–`r details$year_last`). This kind of time series cross-sectional (TSCS) data reflects a natural hierarchical structure, with repeated yearly observations nested within countries ([see this whole guide I wrote](https://www.andrewheiss.com/blog/2021/12/01/multilevel-models-panel-data-guide/) because of this exact project)

```{tikz panel-structure-svg, engine.opts=font_opts}
#| echo: false
#| fig-cap: "Multilevel panel data structure, with yearly observations of $y$ nested in countries"
#| fig-align: center
#| fig-ext: svg
#| out-width: 100%
\usetikzlibrary{positioning}
\usetikzlibrary{shapes.geometric}
\definecolor{red}{HTML}{CC503E}
\definecolor{teal1}{HTML}{2a5674}
\definecolor{teal2}{HTML}{68abb8}
\definecolor{teal3}{HTML}{85c4c9}
\definecolor{teal4}{HTML}{a8dbd9}
\definecolor{peach1}{HTML}{f59e72}
\definecolor{peach2}{HTML}{f8b58b}
\definecolor{peach3}{HTML}{facba6}
\begin{tikzpicture}[{every node/.append style}=draw]
  \node [rectangle,fill=teal2] (country1) at (0, 2.5) {Country 1};
  \node [ellipse,fill=peach1] (y11) at (-1.85, 1) {$y_{i,{t = 1990}_1}$};
  \node [ellipse,fill=peach1] (y21) at (0, 1) {$y_{i,{t = t}_1}$};
  \node [ellipse,fill=peach1] (y31) at (1.85, 1) {$y_{i,{t = 2013}_1}$};
  \draw [-latex] (country1) to (y11);
  \draw [-latex] (country1) to (y21);
  \draw [-latex] (country1) to (y31);

  \node [rectangle,fill=teal3] (country2) at (5.35, 2.5) {Country 2};
  \node [ellipse,fill=peach2] (y12) at (4.15, 1) {$y_{i,{1990}_2}$};
  \node [draw=none] (y22) at (5.35, 1) {$\dots$};
  \node [ellipse,fill=peach2] (y32) at (6.55, 1) {$y_{i,{2013}_2}$};
  \draw [-latex] (country2) to (y12);
  \draw [-latex] (country2) to (y22);
  \draw [-latex] (country2) to (y32);

  \node [draw=none] (dots_top) at (7.85, 2.5) {$\dots$};
  \node [draw=none] (dots_bottom) at (7.85, 1) {$\dots$};
	\draw [-latex] (dots_top) to (dots_bottom);

  \node [rectangle,fill=teal4] (country_142) at (10.6, 2.5) {Country 142};
  \node [ellipse,fill=peach3] (y1_142) at (9.25, 1) {$y_{i,{1990}_{142}}$};
  \node [draw=none] (y2_142) at (10.6, 1) {$\dots$};
  \node [ellipse,fill=peach3] (y3_142) at (11.95, 1) {$y_{i,{2013}_{142}}$};
  \draw [-latex] (country_142) to (y1_142);
  \draw [-latex] (country_142) to (y2_142);
  \draw [-latex] (country_142) to (y3_142);

  \node [rectangle,fill=teal1,text=white] (population) at (5, 4) {Countries eligible for aid};
  \draw [-latex] (population) to (country1);
  \draw [-latex] (population) to (country2);
  \draw [-latex] (population) to (dots_top);
  \draw [-latex] (population) to (country_142);
\end{tikzpicture}
```


```{r plot-biggest-movers}
#| out-width: 80%
biggest_movers <- df_country_aid_laws %>% 
  group_by(country) %>% 
  filter(!any(total_oda == 0)) %>% 
  summarize(across(c(v2csreprss, total_oda), lst(min, max, diff = ~max(.) - min(.))))

top_overall <- top_n(biggest_movers, 15, v2csreprss_diff) %>% 
  filter(country %in% top_n(biggest_movers, 15, total_oda_diff)$country) %>% 
  top_n(3, v2csreprss_diff)

df_cs_oda_highlight <- df_country_aid_laws %>% 
  mutate(highlight_country = ifelse(country %in% top_overall$country, 
                                    country, "Other"),
         highlight_country = factor(highlight_country, ordered = TRUE),
         highlight_country = fct_relevel(highlight_country, "Other", after = Inf)) %>% 
  mutate(highlight = highlight_country != "Other")

ggplot(df_cs_oda_highlight, aes(x = v2csreprss, y = total_oda, group = country)) +
  geom_point(size = 0.15, alpha = 0.15) +
  geom_smooth(method = "lm", aes(group = NULL), color = clrs$Prism[6], 
              linewidth = 1.25, linetype = "21", se = FALSE, formula = y ~ x) +
  geom_path(aes(color = highlight_country, size = highlight),
            arrow = arrow(type = "open", angle = 30, length = unit(0.75, "lines")),
            key_glyph = "timeseries") +
  scale_y_continuous(trans = "log1p", breaks = c(1e7, 1e8, 1e9, 1e10, 1e11),
                     labels = label_dollar(scale_cut = cut_short_scale())) +
  scale_size_manual(values = c(0.075, 1.25), guide = "none") +
  scale_color_manual(values = c(clrs$Prism[2], clrs$Prism[7], clrs$Prism[9], "grey50"),
                     guide = guide_legend(override.aes = list(linewidth = 1))) +
  coord_cartesian(ylim = c(1e7, 1e11)) +
  labs(x = "Civil society repression\n(Higher values represent less repression)",
       y = "Total ODA", color = NULL, size = NULL) +
  theme_donors()
```
