---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)

library(emoji)
```

# Are Donors Really Responding? Analyzing the Impact of Global Restrictions on NGOs

<!-- badges: start -->
<!-- badges: end -->

### `r emoji_glue(":roll_eyes::turtle:")`: Note on "testy turtle" project name

Because project titles change all the time with revisions, rewriting, and peer review, we used [**codename**](http://svmiller.com/codename/) to generate an [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames) internal-to-us project name that won't change. The seed `53879` was generated with random atmospheric noise at [random.org](https://www.random.org/).

```{r generate-code-name, eval=FALSE}
library(codename)
codename_message()
#> code name generated by {codename} v.0.4.0

codename(seed = 53879, type = "ubuntu")
#> [1] "testy turtle"
```


## Licenses

**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)).

**Code:** All code is licensed under the [MIT License](LICENSE.md).


## Contributions and Code of Conduct

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
