---
title: "Causal model and theory"
author: "Suparna Chaudhry and Andrew Heiss"
date: "`r format(Sys.time(), '%F')`"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.retina = 3,
                      tidy.opts = list(width.cutoff = 120),  # For code
                      options(width = 90),  # For output
                      fig.asp = 0.618, fig.width = 7, 
                      fig.align = "center", out.width = "100%")

options(dplyr.summarise.inform = FALSE)
```

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(ggdag)
library(dagitty)
library(here)

withr::with_dir(here::here(), {
  source(tar_read(plot_funs))
  source(tar_read(misc_funs))
})

update_geom_defaults(ggdag:::GeomDagText, list(family = "Noto Sans", face = "plain"))

my_seed <- 1234
set.seed(my_seed)
```


# Full messy model

```{r full-giant-dag, fig.width=10, fig.height=7, fig.asp=NULL}
huge_messy_dag <- dagitty('
dag {
"Corruption[t-1]" [adjusted,pos="7.000,2.000"]
"Corruption[t-i]" [pos="2.000,2.000"]
"Corruption[t]" [pos="12.000,2.000"]
"Democracy[t-1]" [adjusted,pos="7.250,1.000"]
"Democracy[t-i]" [pos="2.250,1.000"]
"Democracy[t]" [pos="12.250,1.000"]
"Disasters[t-1]" [adjusted,pos="7.250,12.000"]
"Disasters[t-i]" [pos="2.250,12.000"]
"Disasters[t]" [pos="12.250,12.000"]
"Education[t-1]" [adjusted,pos="6.250,8.000"]
"Education[t-i]" [pos="1.250,8.000"]
"Education[t]" [pos="11.250,8.000"]
"GDP/capita[t-1]" [adjusted,pos="6.000,6.000"]
"GDP/capita[t-i]" [pos="1.000,6.000"]
"GDP/capita[t]" [pos="11.000,6.000"]
"Health[t-1]" [adjusted,pos="6.500,9.000"]
"Health[t-i]" [pos="1.500,9.000"]
"Health[t]" [pos="11.500,9.000"]
"Mortality[t-1]" [adjusted,pos="6.750,10.000"]
"Mortality[t-i]" [pos="1.750,10.000"]
"Mortality[t]" [pos="11.750,10.000"]
"Outcome[t-1]" [pos="9.000,6.500"]
"Outcome[t-i]" [pos="4.000,6.500"]
"Outcome[t]" [outcome,pos="14.000,6.500"]
"Restrictions[t-1]" [exposure,pos="8.000,7.750"]
"Restrictions[t-i]" [adjusted,pos="3.000,7.750"]
"Restrictions[t]" [pos="13.000,7.750"]
"Trade[t-1]" [adjusted,pos="6.000,7.000"]
"Trade[t-i]" [pos="1.000,7.000"]
"Trade[t]" [pos="11.000,7.000"]
"Violence[t-1]" [adjusted,pos="6.250,5.000"]
"Violence[t-i]" [pos="1.250,5.000"]
"Violence[t]" [pos="11.250,5.000"]
"`Civil liberties`[t-1]" [adjusted,pos="6.500,4.000"]
"`Civil liberties`[t-i]" [pos="1.500,4.000"]
"`Civil liberties`[t]" [pos="11.500,4.000"]
"`Internal conflict`[t-1]" [adjusted,pos="7.000,11.000"]
"`Internal conflict`[t-i]" [pos="2.000,11.000"]
"`Internal conflict`[t]" [pos="12.000,11.000"]
"`Rule of law`[t-1]" [adjusted,pos="6.750,3.000"]
"`Rule of law`[t-i]" [pos="1.750,3.000"]
"`Rule of law`[t]" [pos="11.750,3.000"]
"Corruption[t-1]" -> "Corruption[t]"
"Corruption[t-1]" -> "Outcome[t-1]"
"Corruption[t-1]" -> "Restrictions[t-1]"
"Corruption[t-i]" -> "Corruption[t-1]"
"Corruption[t-i]" -> "Outcome[t-i]"
"Corruption[t-i]" -> "Restrictions[t-i]"
"Corruption[t]" -> "Outcome[t]"
"Corruption[t]" -> "Restrictions[t]"
"Democracy[t-1]" -> "Corruption[t-1]"
"Democracy[t-1]" -> "Democracy[t]"
"Democracy[t-1]" -> "Outcome[t-1]"
"Democracy[t-1]" -> "Restrictions[t-1]"
"Democracy[t-1]" -> "`Rule of law`[t-1]"
"Democracy[t-i]" -> "Democracy[t-1]"
"Democracy[t-i]" -> "Outcome[t-i]"
"Democracy[t-i]" -> "Restrictions[t-i]"
"Democracy[t]" -> "Corruption[t]"
"Democracy[t]" -> "Outcome[t]"
"Democracy[t]" -> "Restrictions[t]"
"Democracy[t]" -> "`Rule of law`[t]"
"Disasters[t-1]" -> "Outcome[t-1]"
"Disasters[t-1]" -> "Restrictions[t-1]"
"Disasters[t-i]" -> "Outcome[t-i]"
"Disasters[t-i]" -> "Restrictions[t-i]"
"Disasters[t]" -> "Outcome[t]"
"Disasters[t]" -> "Restrictions[t]"
"Education[t-1]" -> "Education[t]"
"Education[t-1]" -> "Outcome[t-1]"
"Education[t-1]" -> "Restrictions[t-1]"
"Education[t-i]" -> "Education[t-1]"
"Education[t-i]" -> "Outcome[t-i]"
"Education[t-i]" -> "Restrictions[t-i]"
"Education[t]" -> "Outcome[t]"
"Education[t]" -> "Restrictions[t]"
"GDP/capita[t-1]" -> "GDP/capita[t]"
"GDP/capita[t-1]" -> "Outcome[t-1]"
"GDP/capita[t-1]" -> "Restrictions[t-1]"
"GDP/capita[t-i]" -> "GDP/capita[t-1]"
"GDP/capita[t-i]" -> "Outcome[t-i]"
"GDP/capita[t-i]" -> "Restrictions[t-i]"
"GDP/capita[t]" -> "Outcome[t]"
"GDP/capita[t]" -> "Restrictions[t]"
"Health[t-1]" -> "Health[t]"
"Health[t-1]" -> "Outcome[t-1]"
"Health[t-1]" -> "Restrictions[t-1]"
"Health[t-i]" -> "Health[t-1]"
"Health[t-i]" -> "Outcome[t-i]"
"Health[t-i]" -> "Restrictions[t-i]"
"Health[t]" -> "Outcome[t]"
"Health[t]" -> "Restrictions[t]"
"Mortality[t-1]" -> "Mortality[t]"
"Mortality[t-1]" -> "Outcome[t-1]"
"Mortality[t-1]" -> "Restrictions[t-1]"
"Mortality[t-i]" -> "Mortality[t-1]"
"Mortality[t-i]" -> "Outcome[t-i]"
"Mortality[t-i]" -> "Restrictions[t-i]"
"Mortality[t]" -> "Outcome[t]"
"Mortality[t]" -> "Restrictions[t]"
"Outcome[t-1]" -> "Outcome[t]"
"Outcome[t-i]" -> "Outcome[t-1]"
"Restrictions[t-1]" -> "Outcome[t-1]"
"Restrictions[t-1]" -> "Outcome[t]"
"Restrictions[t-1]" -> "Restrictions[t]"
"Restrictions[t-i]" -> "Outcome[t-1]"
"Restrictions[t-i]" -> "Outcome[t-i]"
"Restrictions[t-i]" -> "Restrictions[t-1]"
"Restrictions[t]" -> "Outcome[t]"
"Trade[t-1]" -> "Outcome[t-1]"
"Trade[t-1]" -> "Restrictions[t-1]"
"Trade[t-1]" -> "Trade[t]"
"Trade[t-i]" -> "Outcome[t-i]"
"Trade[t-i]" -> "Restrictions[t-i]"
"Trade[t-i]" -> "Trade[t-1]"
"Trade[t]" -> "GDP/capita[t]"
"Trade[t]" -> "Outcome[t]"
"Trade[t]" -> "Restrictions[t]"
"Violence[t-1]" -> "Outcome[t-1]"
"Violence[t-1]" -> "Restrictions[t-1]"
"Violence[t-1]" -> "Violence[t]"
"Violence[t-i]" -> "Outcome[t-i]"
"Violence[t-i]" -> "Restrictions[t-i]"
"Violence[t-i]" -> "Violence[t-1]"
"Violence[t]" -> "Outcome[t]"
"Violence[t]" -> "Restrictions[t]"
"`Civil liberties`[t-1]" -> "Outcome[t-1]"
"`Civil liberties`[t-1]" -> "Restrictions[t-1]"
"`Civil liberties`[t-1]" -> "`Civil liberties`[t]"
"`Civil liberties`[t-i]" -> "Outcome[t-i]"
"`Civil liberties`[t-i]" -> "Restrictions[t-i]"
"`Civil liberties`[t-i]" -> "`Civil liberties`[t-1]"
"`Civil liberties`[t]" -> "Outcome[t]"
"`Civil liberties`[t]" -> "Restrictions[t]"
"`Internal conflict`[t-1]" -> "Outcome[t-1]"
"`Internal conflict`[t-1]" -> "Restrictions[t-1]"
"`Internal conflict`[t-1]" -> "`Internal conflict`[t]"
"`Internal conflict`[t-i]" -> "Outcome[t-i]"
"`Internal conflict`[t-i]" -> "Restrictions[t-i]"
"`Internal conflict`[t-i]" -> "`Internal conflict`[t-1]"
"`Internal conflict`[t]" -> "Outcome[t]"
"`Internal conflict`[t]" -> "Restrictions[t]"
"`Rule of law`[t-1]" -> "Outcome[t-1]"
"`Rule of law`[t-1]" -> "Restrictions[t-1]"
"`Rule of law`[t-1]" -> "`Rule of law`[t]"
"`Rule of law`[t-i]" -> "Outcome[t-i]"
"`Rule of law`[t-i]" -> "Restrictions[t-i]"
"`Rule of law`[t-i]" -> "`Rule of law`[t-1]"
"`Rule of law`[t]" -> "Outcome[t]"
"`Rule of law`[t]" -> "Restrictions[t]"
}
')

huge_messy_dag_plot <- huge_messy_dag %>% 
  tidy_dagitty() %>% 
  mutate(var_type = case_when(
    str_detect(name, "Outcome") ~ "Outcome",
    str_detect(name, "Restrictions") ~ "Restrictions",
    TRUE ~ "Z"
  )) %>% 
  mutate(time_period = case_when(
    str_detect(name, "t-1") ~ 2,
    str_detect(name, "t-i") ~ 1,
    TRUE ~ 3
  )) %>% 
  mutate(arrow_color = case_when(
    name == "Restrictions[t-1]" & to == "Outcome[t]" ~ "#FF4136",
    TRUE ~ "grey60"
  ))

ggplot(huge_messy_dag_plot, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_edges(aes(edge_colour = arrow_color)) +
  geom_dag_point(aes(color = var_type, alpha = time_period), size = 12) +
  geom_dag_text(data = filter(huge_messy_dag_plot, var_type == "Outcome"),
                color = "black", size = pts(9), parse = TRUE) +
  geom_dag_text(data = filter(huge_messy_dag_plot, var_type == "Restrictions"),
                color = "black", size = pts(9), parse = TRUE) +
  geom_dag_text(data = filter(huge_messy_dag_plot, var_type == "Z"),
                color = "black", size = pts(9), parse = TRUE) +
  scale_color_manual(values = c("#B10DC9", "#FF851B", "grey60")) +
  scale_y_reverse() +
  guides(alpha = FALSE, color = FALSE) +
  theme_dag()
```


# Simpler model with families of confounders

```{r simplerish-dag, fig.width=10.5, fig.height=4.5, fig.asp=NULL}
simplerish_dag <- dagitty('
dag {
"`Human rights & politics`[t-1]" [adjusted,pos="5,1.5"]
"`Human rights & politics`[t-i]" [pos="1,1.5"]
"`Human rights & politics`[t]" [pos="9,1.5"]
"`Economics & development`[t-1]" [adjusted,pos="5,2.5"]
"`Economics & development`[t-i]" [pos="1,2.5"]
"`Economics & development`[t]" [pos="9,2.5"]
"Outcome[t-1]" [pos="6.5,1.75"]
"Outcome[t-i]" [adjusted,pos="2.5,1.75"]
"Outcome[t]" [outcome,pos="10.5,1.75"]
"Restrictions[t-1]" [exposure,pos="6,2.25"]
"Restrictions[t-i]" [adjusted,pos="2,2.25"]
"Restrictions[t]" [pos="10,2.25"]
"`Unexpected shocks`[t-1]" [adjusted,pos="5,2"]
"`Unexpected shocks`[t-i]" [pos="1,2"]
"`Unexpected shocks`[t]" [pos="9,2"]
"`Human rights & politics`[t-1]" -> "`Human rights & politics`[t]"
"`Human rights & politics`[t-1]" -> "Outcome[t-1]"
"`Human rights & politics`[t-1]" -> "Restrictions[t-1]"
"`Human rights & politics`[t-1]" -> "Restrictions[t]"
"`Human rights & politics`[t-i]" -> "`Human rights & politics`[t-1]"
"`Human rights & politics`[t-i]" -> "Outcome[t-i]"
"`Human rights & politics`[t-i]" -> "Restrictions[t-i]"
"`Human rights & politics`[t]" -> "Outcome[t]"
"`Human rights & politics`[t]" -> "Restrictions[t]"
"`Economics & development`[t-1]" -> "`Economics & development`[t]"
"`Economics & development`[t-1]" -> "Outcome[t-1]"
"`Economics & development`[t-1]" -> "Restrictions[t-1]"
"`Economics & development`[t-1]" -> "Restrictions[t]"
"`Economics & development`[t-i]" -> "`Economics & development`[t-1]"
"`Economics & development`[t-i]" -> "Outcome[t-i]"
"`Economics & development`[t-i]" -> "Restrictions[t-i]"
"`Economics & development`[t]" -> "Outcome[t]"
"`Economics & development`[t]" -> "Restrictions[t]"
"Outcome[t-1]" -> "Outcome[t]"
"Outcome[t-1]" -> "Restrictions[t]"
"Outcome[t-i]" -> "Outcome[t-1]"
"Outcome[t-i]" -> "Restrictions[t-1]"
"Restrictions[t]" -> "Outcome[t]"
"Restrictions[t-1]" -> "Outcome[t-1]"
"Restrictions[t-i]" -> "Outcome[t-i]"
"Restrictions[t-1]" -> "Outcome[t]"
"Restrictions[t-1]" -> "Restrictions[t]"
"Restrictions[t-i]" -> "Outcome[t-1]"
"Restrictions[t-i]" -> "Restrictions[t-1]"
"`Unexpected shocks`[t-1]" -> "Outcome[t-1]"
"`Unexpected shocks`[t-1]" -> "Restrictions[t-1]"
"`Unexpected shocks`[t-1]" -> "Restrictions[t]"
"`Unexpected shocks`[t-1]" -> "`Unexpected shocks`[t]"
"`Unexpected shocks`[t-i]" -> "Outcome[t-i]"
"`Unexpected shocks`[t-i]" -> "Restrictions[t-i]"
"`Unexpected shocks`[t-i]" -> "`Unexpected shocks`[t-1]"
"`Unexpected shocks`[t]" -> "Outcome[t]"
"`Unexpected shocks`[t]" -> "Restrictions[t]"
}
')

simplerish_dag_plot <- simplerish_dag %>% 
  tidy_dagitty() %>% 
  mutate(var_type = case_when(
    str_detect(name, "Outcome") ~ "Outcome",
    str_detect(name, "Restrictions") ~ "Restrictions",
    TRUE ~ "Z"
  )) %>% 
  mutate(time_period = case_when(
    str_detect(name, "t-1") ~ 2,
    str_detect(name, "t-i") ~ 1,
    TRUE ~ 3
  )) %>% 
  mutate(arrow_color = case_when(
    name == "Restrictions[t-1]" & to == "Outcome[t]" ~ "#FF4136",
    TRUE ~ "grey60"
  ))

ggplot(simplerish_dag_plot, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_edges(aes(edge_colour = arrow_color)) +
  geom_dag_point(aes(color = var_type, alpha = time_period), size = 12) +
  geom_dag_text(data = filter(simplerish_dag_plot, var_type == "Outcome"),
                color = "black", size = pts(9), parse = TRUE) +
  geom_dag_text(data = filter(simplerish_dag_plot, var_type == "Restrictions"),
                color = "black", size = pts(9), parse = TRUE) +
  geom_dag_text(data = filter(simplerish_dag_plot, var_type == "Z"),
                color = "black", size = pts(9), parse = TRUE) +
  scale_color_manual(values = c("#B10DC9", "#FF851B", "grey60")) +
  scale_y_reverse() +
  guides(alpha = FALSE, color = FALSE) +
  theme_dag()
```


# Simplest model

```{r simple-dag, fig.width=7, fig.height=3.75, fig.asp=NULL}
simple_dag <- dagitty('
dag {
"Outcome[t-i]" [pos="1.5,2"]
"Outcome[t-1]" [pos="3.5,2"]
"Outcome[t]" [outcome,pos="6,2"]
"Restrictions[t-i]" [pos="1,1"]
"Restrictions[t-1]" [exposure,pos="3,1"]
"Restrictions[t]" [pos="5,1"]
"Z[t-i]" [pos="1,3"]
"Z[t-1]" [pos="3,3"]
"Z[t]" [pos="5,3"]
"Outcome[t-1]" -> "Outcome[t]"
"Outcome[t-1]" -> "Restrictions[t]"
"Outcome[t-i]" -> "Outcome[t-1]"
"Outcome[t-i]" -> "Restrictions[t-1]"
"Restrictions[t]" -> "Outcome[t]"
"Restrictions[t-1]" -> "Outcome[t-1]"
"Restrictions[t-i]" -> "Outcome[t-i]"
"Restrictions[t-1]" -> "Outcome[t]"
"Restrictions[t-1]" -> "Restrictions[t]"
"Restrictions[t-i]" -> "Outcome[t-1]"
"Restrictions[t-i]" -> "Restrictions[t-1]"
"Z[t-1]" -> "Outcome[t-1]"
"Z[t-1]" -> "Restrictions[t-1]"
"Z[t-1]" -> "Restrictions[t]"
"Z[t-1]" -> "Z[t]"
"Z[t-i]" -> "Outcome[t-i]"
"Z[t-i]" -> "Restrictions[t-1]"
"Z[t-i]" -> "Restrictions[t-i]"
"Z[t-i]" -> "Z[t-1]"
"Z[t]" -> "Outcome[t]"
"Z[t]" -> "Restrictions[t]"
}
') 

simple_dag_plot <- simple_dag %>% 
  tidy_dagitty() %>% 
  mutate(var_type = case_when(
    str_detect(name, "Outcome") ~ "Outcome",
    str_detect(name, "Restrictions") ~ "Restrictions",
    str_detect(name, "Z") ~ "Z"
  )) %>% 
  mutate(time_period = case_when(
    str_detect(name, "t-1") ~ 2,
    str_detect(name, "t-i") ~ 1,
    TRUE ~ 3
  )) %>% 
  mutate(arrow_color = case_when(
    name == "Restrictions[t-1]" & to == "Outcome[t]" ~ "#FF4136",
    TRUE ~ "grey60"
  )) %>% 
  mutate(letter_only = case_when(
    str_detect(name, "Outcome") ~ str_replace(name, "Outcome", "Y"),
    str_detect(name, "Restrictions") ~ str_replace(name, "Restrictions", "X"),
    TRUE ~ name
  ))

simple_dag_out <- ggplot(simple_dag_plot, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_edges(aes(edge_colour = arrow_color)) +
  geom_dag_point(aes(color = var_type, alpha = time_period), size = 12) +
  geom_dag_text(data = filter(simple_dag_plot, var_type == "Outcome"),
                color = "black", size = pts(11), parse = TRUE, 
                nudge_y = 0.2, nudge_x = 0.3) +
  geom_dag_text(data = filter(simple_dag_plot, var_type == "Restrictions"),
                color = "black", size = pts(11), parse = TRUE, 
                nudge_y = -0.25) +
  geom_dag_text(data = filter(simple_dag_plot, var_type == "Z"),
                color = "black", size = pts(11), parse = TRUE,
                nudge_y = 0) +
  scale_color_manual(values = c("#B10DC9", "#FF851B", "grey60")) +
  guides(alpha = FALSE, color = FALSE) +
  theme_dag()
simple_dag_out
```

```{r simple-dag-letters, fig.width=7, fig.height=3.75, fig.asp=NULL}
simple_dag_letters_out <- ggplot(simple_dag_plot, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_edges(aes(edge_colour = arrow_color)) +
  geom_dag_point(aes(color = var_type, alpha = time_period), size = 12) +
  geom_dag_text(aes(label = letter_only),
                color = "black", size = pts(11), parse = TRUE) +
  scale_color_manual(values = c("#B10DC9", "#FF851B", "grey60")) +
  guides(alpha = FALSE, color = FALSE) +
  theme_dag()
simple_dag_letters_out

ggsave(here("analysis", "output", "dag_simple_letters.pdf"), simple_dag_letters_out,
       width = 7, height = 3.75, device = cairo_pdf)
ggsave(here("analysis", "output", "dag_simple_letters.png"), simple_dag_letters_out,
       width = 7, height = 3.75, dpi = 300, type = "cairo")
```



# Adjustment sets

These DAGs are complex—especially the one with every possible node. However, they have important analytical value. We cannot randomly assign countries to impose anti-NGO laws or restrict the environment for civil society—doing that is completely infeasable (and unethical!). This means that we cannot use experimental data to measure the causal effect of anti-NGO restrictions on foreign aid, or $E[\text{Aid} \mid do(\text{Restrictions})]$. We also don't have any quasi-experimental situations that would allow for context-based identification of the effect of restrictions on aid.

Simply measuring $E[\text{Aid} \mid \text{Restrictions}]$ is trivial—just run `lm(aid ~ restrictions)` and look at the coefficient. However, this estimate cannot be interpreted in any sort of causal way, since correlation is not causation. Using the logic of *do*-calculus, we can actually use the relationships between the nodes in the DAG to transform $E[\text{Aid} \mid do(\text{Restrictions})]$ into a *do*-free expression by making statistical adjustments and closing backdoor pathways that open up spurious relationships between restrictions and aid. As long as we can find a minimally sufficient adjustment set—or a set of nodes or variables that need to be adjusted in order to ensure that restrictions is *d*-separated from aid—we can isolate and identify the causal link between restrictions and aid.

Rather than go through the complex math behind the three rules of *do*-calculus, we can use R (or dagitty.net) to identify minimal sufficient adjustment sets based on the three DAGs above.

- Huge complicated DAG:

```{r huge-dag-adjustment, indent="    ", class.source = 'fold-show'}
huge_messy_dag %>%
  adjustmentSets()
```

- Simpler-ish DAG:

```{r simplerish-dag-adjustment, indent="    ", class.source = 'fold-show'}
simplerish_dag %>%
  adjustmentSets()
```

- Simple DAG:

```{r simple-dag-adjustment, indent="    ", class.source = 'fold-show'}
simple_dag %>%
  adjustmentSets()
```

\ 

In other words, if we want to isolate the causal effect of anti-NGO restrictions in time $t$ on aid in time $t+1$ (i.e. the effect of lagged restrictions), we need to adjust for lagged aid ($t-1$), lagged restrictions ($t-1$), and time-varying confounders ($t$). 

Fortunately, marginal structural models allow us to make all of these adjustments using special inverse probability weights that take this lagging structure and treatment history into account.

$$
\text{Continuous stabilized IPW}_{it} = \prod^t_{t = 1} \frac{f_{X | \bar{X}, V}[(X_{it} | \bar{X}_{i, t-1}, V_i); \mu_1, \sigma^2_1]}{f_{X | \bar{X}, Y, Z, V}[(X_{it} | \bar{X}_{i, t-1}, Y_{i, t-1}, Z_{it}, V_i), \mu_2, \sigma^2_2]}
$$

- The numerator contains the probability of the observed treatment status ($X_{it}$) at each time given the previous history of treatment ($\bar{X}_{i, t-1}$) and time invariant confounders ($V_i$). 
- The denominator contains the probability of the observed treatment status ($X_{it}$) at each time given the previous history of treatment ($\bar{X}_{i, t-1}$), previous outcome ($Y_{i, t-1}$), time *varying* confounders ($Z_{it}$), and time *invariant* confounders ($V_i$).
- These two probability distributions have a mean of $\mu_{1, 2}$ and variance of $\sigma^2_{1, 2}$.

Finally, these weights are used in an outcome model similar to this:

```{r eval=FALSE, class.source = 'fold-show'}
lm(outcome ~ lag_treatment, weights = ipw)
```

Doing this process closes the backdoor pathways between lagged restrictions and present aid and is theoretically sufficient for isolating the causal link between the two.


# Final variables to use

Based on these DAGs, here are the variables we use in our treatment and outcome models:

- **Outcome**
  - H~1~: log aid in $t$ (`total_oda_lead` and `total_oda_log_lead`)
  - H~2~: proportion of aid given for contentious causes in $t$ (`prop_contentious`)
  - H~3~: proportion of aid given to domestic/international NGOS in $t$ (`prop_ngo_dom` and `prop_ngo_foreign`)
- **Treatment**
  - Anti-civil society laws and general restrictive environment in $t-1$ (`barriers_total` and `v2xcs_ccsi`)
- **Time-varying confounders** (all in $t-1$)
  - Human rights and politics
    - Electoral democracy: `v2x_polyarchy`
    - Corruption: `v2x_corr`
    - Rule of law: `v2x_rule`
    - Civil liberties index: `v2x_civlib`
    - Physical violence index: `v2x_clphy`
    - Private civil liberties index: `v2x_clpriv`
  - Economics and development
    - Wealth: `gdpcap_log`
    - International trade: `un_trade_pct_gdp`
    - Educational equality: `v2peedueq`
    - Health equality: `v2pehealth`
    - Infant mortality rate: `e_peinfmor`
  - Unexpected shocks
    - Internal conflict: `internal_conflict_past_5`
    - Natural disasters: `natural_dis_count`
- **Time-invarying confounders**
  - Country code included as multilevel random effects(`(1 | gwcode)`)
